---
title             : "Sociolinguistic development in a diverse, multilingual environment"
shorttitle        : "Sociolinguistic development"

author: 
  - name          : "Ruthe Foushee"
    affiliation   : "1,2"
    corresponding : yes   
    address       : "University Ave., Chicago, IL 60637"
    email         : "foushee@uchicago.edu"
  - name          : "Roya Baharloo"
    affiliation   : "1"
  - name          : "Mahesh Srinivasan"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of California, Berkeley"
  - id            : "2"
    institution   : "University of Chicago"

authornote: |
  Ruthe Foushee
  Department of Psychology
  XXXX University Ave.
  Chicago, IL 60637
  
  Roya Baharloo
  Department of Psychology
  2121 Berkeley Way West
  Berkeley, CA 94701
  
  Mahesh Srinivasan
  srinivasan@berkeley.edu
  Department of Psychology
  2121 Berkeley Way West
  Berkeley, CA 94701


abstract: |

  Stronger associations when responding to _name_ of language, rather than audio clip of, suggesting greater role for cultural transmission than statistical learning.
  
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```


# Methods

## Participants
XXX students participated in this study, recruited from an English-medium school in Gujarat, IN. 
We tested students from the X, Y, Z standards.

## Material
## Procedure

### Stereotypical Speakers
### Associations
### Essentialism and Learning
### Language Identification

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
