---
title: "India Sociolinguistics Face Selection Analyses"
author: "Ruthe Foushee"
date: "2023-08-17"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r wealth-setup, include=FALSE}
library(here)
here::i_am('2_face_selections/2_face-selections.Rmd')

knitr::opts_chunk$set(
  echo = FALSE, message=F, warning=F,
  fig.width = 6)

source(here('isl-resources.R'))
```

```{r read-in-data}
f <- read.csv(here('data/r_dfs/face_selection_data.csv'))[,-1]

factor_vars <- c('study_name', 'id', 'child_sex', 'child_religion', 
                 'school', 'standard',
                 'question_type', 'presentation',
                 'language', 'speaker_gender', 
                 'face', 'army_navy_language')

numeric_vars <- c('standard_num', 'child_age_centered', 'child_age_centered', 
                  'sequence')

f <- f %>%
  mutate_at(factor_vars, as.factor) %>%
  mutate_at(numeric_vars, as.numeric)

f <- f %>%
  filter(face!="")
```

```{r faces-setup, include=FALSE}
f$language <- relevel(f$language, ref="Gujarati")
f$face <- relevel(f$face, ref="hindu")
f$num_faces <- f$hindu_face + f$muslim_face + f$dravidian_face +
  f$asian_face + f$white_face

fl <-f[f$presentation=="label",]
fl$language <- factor(fl$language, levels=c("Gujarati", 
                                            "Hindi", "Urdu", "Marathi", "Tamil", "English", "Mandarin"))

#write.csv(fl, here('data/r_dfs/faces_data_by_language_label.csv'))
```

```{r how-many-faces, include=F}
#table("std"=f$standard, "num faces"=f$num_faces)
num_face_summary_tab <- f %>% 
  ungroup() %>%
  mutate(n=n()) %>%
  filter(!is.na(num_faces)) %>%
  group_by(num_faces, n) %>%
  reframe(n_face_count = n(),
            percent_selection = n_face_count/n) %>%
  distinct(.)

num_face_std_summary_tab <- f %>% 
  filter(!is.na(num_faces)) %>%
  group_by(standard) %>%
  mutate(n=n()) %>% 
  group_by(standard, num_faces, n) %>%
  reframe(n_face_count = n(),
            percent_selection = n_face_count/n) %>%
  distinct(.)

nfp <- ggplot(num_face_std_summary_tab, 
       aes(x=num_faces, y=percent_selection)) +
  geom_bar(stat="identity") +
  facet_grid(~standard) +
  sans_theme +
  ylab("percent of selections") +
  xlab("# faces selected") +
  sans_axes_theme +
    labs(title="Number of Faces Selected by Standard")

#table(f$num_faces>1) #90 trials more than one face
#length(unique(f[f$num_faces>1,]$id)) #24 kids

# table(f$face) # 69 no-opinion trials
# length(unique(f[f$face=="idk",]$id)) # 36 kids
```

```{r no-face,include=F}
f %>%
  group_by(id, question_type, presentation, speaker_gender, language, sequence) %>%
  mutate(num_opt_outs = sum(no_opinion_face)) %>%
  group_by(standard) %>%
  summarize(num_opt_outs = sum(num_opt_outs)/n()) %>%
  kable(.) 

length(unique(f[f$no_opinion_face==1,]$id))
```
...and rarely 'opted out'

# Face Preferences

## Language Presented in Audio Clip

*Who could be speaking?* 

Children across standards tended to select a single face in response to the face selection questions (95\% of trials in 3rd standard, 89\% of trials in 5th standard, and 90\% of trials in 7th standard; 91\% overall). Twenty-two children selected more than one face across 53 trials (10 for both Hindi and Urdu, 7 for U.S English, Indian English, and Marathi, 5 for Tamil, 4 for Gujarati, and 3 for Mandarin).
Twenty-nine children selected ``no opinion'' on 39 trials (13 for Mandarin, 11 for Tamil, 6 for Marathi, 3 for Gujarati and Urdu, 2 for U.S. English, and 1 for Hindi). 

Children exhibited a preference for 1-2 faces as speakers for most languages they heard in audio clips. 

## Language Presented by Name

*Who speaks [LANGUAGE]?*

Children exhibited a preference for 1-2 faces as speakers for most languages they were asked about by name. 

## Over Time 

### By Standard (Grade)

#### in Audio Clip

#### by Language Name

Selective face preferences tended to get stronger with age for both auditorily presented and named languages (a greater and greater proportion of children chose the same face(s) as speakers of a given audio clip, or for a given named language).

## By Age

### in Audio Clip

## Models: Odds of Face Selection

### AUDIO

```{r audio-opt-out-more-than-1}
table(f[f$presentation=="audio",]$num_faces>1) #51 trials more than one face
length(unique(f[f$presentation=="audio" & f$num_faces>1,]$id)) #21 kids

table(f[f$presentation=="audio",]$face) # 39 no-opinion trials
length(unique(f[f$presentation=="audio" & f$no_opinion_face==1,]$id)) # 29 kids
table(unique(f[f$presentation=="audio" & f$face=="idk",]$language)) 
```

#### Hindu face (from audio clip)

```{r audio-hindu-glm, include=F}
options(scipen=1000)
fa <- f[f$presentation=="audio",]
fa$language <- factor(fa$language, levels=language_labels)
#write.csv(fa, here('data/r_dfs/faces_data_by_language_audio.csv'))

audio_face_hindu_glm <- glm(
  hindu_face ~ child_age_centered + language, 
  family="binomial", fa)

audio_face_hindu_glm_coefs <- cbind(round(exp(coef(audio_face_hindu_glm)), 2), round(exp(confint(audio_face_hindu_glm)), 2))
```

```{r audio-hindu-int-glm}
fa %>%
  group_by(language, standard) %>%
  summarize(mean=na.mean(hindu_face))

fa %>%
  group_by(language, standard) %>%
  summarize(mean=na.mean(asian_face))

fl %>%
  group_by(language) %>%
  summarize(mean=na.mean(hindu_face))

audio_face_hindu_int_glm <- glm(
  hindu_face ~ child_age_centered*language, 
  family="binomial", fa)

audio_face_hindu_int_glm_coefs <- as.data.frame(cbind(round(exp(coef(audio_face_hindu_int_glm)), 2),
round(exp(confint(audio_face_hindu_int_glm)), 2)))

audio_face_hindu_int_glm_coefs$toss <- audio_face_hindu_int_glm_coefs$`2.5 %`<1 & audio_face_hindu_int_glm_coefs$`97.5 %`>1

audio_face_hindu_int_glm_coefs %>%filter(toss==0)

Anova(audio_face_hindu_int_glm)
```

There was a significant interaction between child age and language ($`r reportAnova(audio_face_hindu_int_glm, "child_age_centered:language")`$), such that as children got older, they increasingly selected the hindu face for Hindi ($`r reportORs(audio_face_hindu_int_glm_coefs, "child_age_centered:languageHindi")`$), 
Urdu ($`r reportORs(audio_face_hindu_int_glm_coefs, "child_age_centered:languageUrdu")`$), 
Gujarati ($`r reportORs(audio_face_hindu_int_glm_coefs, "child_age_centered")`$),
Marathi ($`r reportORs(audio_face_hindu_int_glm_coefs, "child_age_centered:languageMarathi")`$),
Tamil ($`r reportORs(audio_face_hindu_int_glm_coefs, "child_age_centered:languageTamil")`$), and
Indian English ($`r reportORs(audio_face_hindu_int_glm_coefs, "child_age_centered:languageEnglish (India)")`$), and 
decreasingly selected it in response to clips of Mandarin ($`r reportORs(audio_face_hindu_int_glm_coefs, "child_age_centered:languageMandarin")`$).

#### Muslim face (from audio clip)

```{r audio-muslim-glm, include=F}
#audio_face_muslim_glmer <- glmer(
#  muslim_face ~ child_age_centered + language + (1|id), 
#  family="binomial", f[f$presentation=="audio",])

#cbind(round(exp(fixef(audio_face_muslim_glmer)), 2),
#round(exp(confint(audio_face_muslim_glmer)), 2))

audio_face_muslim_glm <- glm(
  muslim_face ~ child_age_centered + language, 
  family="binomial", fa)

audio_face_muslim_glm_coefs <- cbind(round(exp(coef(audio_face_muslim_glm)), 2),
round(exp(confint(audio_face_muslim_glm)), 2))
```

```{r audio-muslim-int-glm}
audio_face_muslim_int_glm <- glm(
  muslim_face ~ child_age_centered*language, 
  family="binomial", fa)

audio_face_muslim_int_glm_coefs <- as.data.frame( cbind(round(exp(coef(audio_face_muslim_int_glm)), 2),
round(exp(confint(audio_face_muslim_int_glm)), 2))
)

audio_face_muslim_int_glm_coefs$toss <- audio_face_muslim_int_glm_coefs$`2.5 %`<1 & audio_face_muslim_int_glm_coefs$`97.5 %`>1

audio_face_muslim_int_glm_coefs %>%filter(toss==0)

Anova(audio_face_muslim_int_glm)

fa%>% group_by(language,standard) %>%
  summarize(mean=na.mean(muslim_face))

#, such that as children got older, they increasingly selected the hindu face for Indian English ($`r reportORs(audio_face_muslim_int_glm_coefs, "child_age_centered:languageEnglish (India)"`$)$), Hindi ($`r reportORs(audio_face_muslim_int_glm_coefs, "child_age_centered:languageHindi")`$), Gujarati ($`r reportORs(audio_face_muslim_int_glm_coefs, "child_age_centered:languageGujarati")`$),  Tamil ($`r reportORs(audio_face_muslim_int_glm_coefs, "child_age_centered:languageTamil")`$), and Urdu ($`r reportORs(audio_face_muslim_int_glm_coefs, "child_age_centered:languageUrdu")`$), and decreasingly selected it in response to clips of Mandarin ($`r reportORs(audio_face_muslim_int_glm_coefs, "child_age_centered")`$), U.S. English .
```

There were significant effects of language ($`r reportAnova(audio_face_muslim_int_glm, "language")`$) and its interaction with child age ($`r reportAnova(audio_face_muslim_int_glm, "child_age_centered:language")`$). 
Children tended to select the muslim face as a speaker of Urdu (52\% of trials overall; $`r reportORs(audio_face_muslim_int_glm_coefs, "languageUrdu")`$), and not to select the muslim face as a speaker of Gujarati (12\% of trials; $`r reportORs(audio_face_muslim_int_glm_coefs, "languageGujarati")`$), Mandarin (3\% of trials; $`r reportORs(audio_face_muslim_int_glm_coefs, "languageMandarin")`$), and Marathi (6\% of trials; $`r reportORs(audio_face_muslim_int_glm_coefs, "languageMarathi")`$). 
As children got older, they associated the muslim face with Gujarati even less (35\% of trials in 3rd grade to 6\% in 7th; $`r reportORs(audio_face_muslim_int_glm_coefs, "child_age_centered:languageGujarati")`$), and 
increased their relative selection of it as the speaker of the Hindi (42\% of trials in 3rd grade to 61\% in 7th; $`r reportORs(audio_face_muslim_int_glm_coefs, "child_age_centered:languageHind")`$), Urdu (48\% of trials in 3rd grade to 59\% in 7th; $`r reportORs(audio_face_muslim_int_glm_coefs, "child_age_centered:languageUrdu")`$), and Indian English ($`r reportORs(audio_face_muslim_int_glm_coefs, "child_age_centered:languageEnglish (India)")`$) audio clips. 

#### Dravidian face (from audio clip)

```{r audio-dravidian-glm, include=F}
audio_face_dravidian_glm <- glm(
  dravidian_face ~ child_age_centered + language, 
  family="binomial", fa)

audio_face_dravidian_glm_coefs <-
  cbind(round(exp(coef(audio_face_dravidian_glm)), 2),
        round(exp(confint(audio_face_dravidian_glm)), 2))
```

```{r audio-dravidian-int-glm}
audio_face_dravidian_int_glm <- glm(
  dravidian_face ~ child_age_centered*language, 
  family="binomial", fa)

audio_face_dravidian_int_glm_coefs <- as.data.frame(
  cbind(round(exp(coef(audio_face_dravidian_int_glm)), 2),
        round(exp(confint(audio_face_dravidian_int_glm)), 2))
)

audio_face_dravidian_int_glm_coefs$toss <- audio_face_dravidian_int_glm_coefs$`2.5 %`<1 & audio_face_dravidian_int_glm_coefs$`97.5 %`>1

audio_face_dravidian_int_glm_coefs %>%filter(toss==0)

Anova(audio_face_dravidian_int_glm)
#Gujarati ($`r reportORs(audio_face_dravidian_int_glm_coefs, "child_age_centered")`$), 
# Hindi ($`r reportORs(audio_face_dravidian_int_glm_coefs, "child_age_centered:languageHindi")`$), 
```

There was a significant effect of language ($`r reportAnova(audio_face_dravidian_int_glm, "language")`$), such that children were unlikely to select the dravidian face as a speaker of Mandarin ($`r reportORs(audio_face_dravidian_int_glm_coefs, "languageMandarin")`$), 
Gujarati ($`r reportORs(audio_face_dravidian_int_glm_coefs, "(Intercept)")`$), 
Indian English ($`r reportORs(audio_face_dravidian_int_glm_coefs, "languageEnglish (India)")`$), Hindi ($`r reportORs(audio_face_dravidian_int_glm_coefs, "languageHindi")`$), or
U.S. English ($`r reportORs(audio_face_dravidian_int_glm_coefs, "languageEnglish (U.S.)")`$),
and likely to select it as a speaker of Marathi ($`r reportORs(audio_face_dravidian_int_glm_coefs, "languageMarathi")`$). 
A significant interaction between child age and language  ($`r reportAnova(audio_face_dravidian_int_glm, "child_age_centered:language")`$), further revealed that as children got older, they increasingly selected the dravidian face in response to clips of 
Tamil ($`r reportORs(audio_face_dravidian_int_glm_coefs, "child_age_centered:languageTamil")`$) and Marathi ($`r reportORs(audio_face_dravidian_int_glm_coefs, "child_age_centered:languageMarathi")`$), and decreasingly in response to Gujarati ($`r reportORs(audio_face_dravidian_int_glm_coefs, "child_age_centered")`$) and Mandarin ($`r reportORs(audio_face_hindu_int_glm_coefs, "child_age_centered:languageMandarin")`$). 

#### East Asian face (from audio clip)

```{r audio-asian-glm, include=F}
audio_face_asian_glm <- glm(
  asian_face ~ child_age_centered + language, 
  family="binomial", fa)

audio_face_asian_glm_coefs <- cbind(round(exp(coef(audio_face_asian_glm)), 2),
round(exp(confint(audio_face_asian_glm)), 2))
```

```{r audio-asian-int-glm}
audio_face_asian_int_glm <- glm(
  asian_face ~ child_age_centered*language, 
  family="binomial", fa)

audio_face_asian_int_glm_coefs <- as.data.frame(
  cbind(round(exp(coef(audio_face_asian_int_glm)), 2),
        round(exp(confint(audio_face_asian_int_glm)), 2))
)

audio_face_asian_int_glm_coefs$toss <- 
  audio_face_asian_int_glm_coefs$`2.5 %`<1 &
  audio_face_asian_int_glm_coefs$`97.5 %`>1

audio_face_asian_int_glm_coefs %>%filter(toss==0)

Anova(audio_face_asian_int_glm)
```

There was a significant effect of language ($`r reportAnova(audio_face_asian_int_glm, "language")`$), such that children were likely to select the asian face as the speaker of Mandarin ($`r reportORs(audio_face_asian_int_glm_coefs, "languageMandarin")`$), Tamil ($`r reportORs(audio_face_asian_int_glm_coefs, "languageTamil")`$), U.S. English ($`r reportORs(audio_face_asian_int_glm_coefs, "languageEnglish (U.S.)")`$), and Indian English ($`r reportORs(audio_face_asian_int_glm_coefs, "languageEnglish (India)")`$), and unlikely to select the asian face as the speaker of Gujarati ($`r reportORs(audio_face_asian_int_glm_coefs, "(Intercept)")`$).
We also saw a significant interaction between language and child age ($`r reportAnova(audio_face_asian_int_glm, "child_age_centered:language")`$), such that as children got older, they increasingly selected the east asian face for 
Mandarin ($`r reportORs(audio_face_asian_int_glm_coefs, "child_age_centered:languageMandarin")`$).

#### White face (from audio clip)

```{r audio-white-glm, include=F}
audio_face_white_glm <- glm(
  white_face ~ child_age_centered + language, 
  family="binomial", fa)

audio_face_white_glm_coefs <- 
  cbind(round(exp(coef(audio_face_white_glm)), 2),
        round(exp(confint(audio_face_white_glm)), 2)) 
```

```{r audio-white-int-glm}
audio_face_white_int_glm <- glm(
  white_face ~ child_age_centered*language, 
  family="binomial", fa)

audio_face_white_int_glm_coefs <- as.data.frame(
  cbind(round(exp(coef(audio_face_white_int_glm)), 2),
        round(exp(confint(audio_face_white_int_glm)), 2))
)

audio_face_white_int_glm_coefs$toss <- 
  audio_face_white_int_glm_coefs$`2.5 %`<1 &
  audio_face_white_int_glm_coefs$`97.5 %`>1

audio_face_white_int_glm_coefs %>% filter(toss==0)

Anova(audio_face_white_int_glm)
```

There was a significant effect of language ($`r reportAnova(audio_face_white_int_glm, "language")`$), such that children rarely selected the white face as a speaker of Gujarati (4\% of trials; $`r reportORs(audio_face_white_int_glm_coefs, "(Intercept)")`$), and selected it as a speaker of either English (Indian, 70\% of trials; $`r reportORs(audio_face_white_int_glm_coefs, "languageEnglish (India)")`$; U.S., 65\% of trials; $`r reportORs(audio_face_white_int_glm_coefs, "languageEnglish (U.S.)")`$), Mandarin (12\% of trials; $`r reportORs(audio_face_white_int_glm_coefs, "languageMandarin")`$) and Tamil (16\% of trials; $`r reportORs(audio_face_white_int_glm_coefs, "languageTamil")`$). 
There was a significant interaction between child age and language ($`r reportAnova(audio_face_white_int_glm, "child_age_centered:language")`$), such that as children got older, they increasingly selected the white face for 
Indian English ($`r reportORs(audio_face_white_int_glm_coefs, "child_age_centered:languageEnglish (India)")`$) and 
U.S. English ($`r reportORs(audio_face_asian_int_glm_coefs, "child_age_centered:languageEnglish (U.S.)")`$).

### LANGUAGE NAME

```{r label-opt-out-more-than-1}
table(f[f$presentation=="label",]$num_faces>1) #37 trials more than one face
length(unique(f[f$presentation=="label" & f$num_faces>1,]$id)) #14 kids

table(f[f$presentation=="label",]$face) # 30 no-opinion trials
length(unique(f[f$presentation=="label" & f$no_opinion_face==1,]$id)) # 14 kids
table(unique(f[f$presentation=="label" & f$no_opinion_face==1,]$language))
```

#### Hindu face (from language name)

```{r label-hindu-glm, include=F}
label_face_hindu_glm <- glm(
  hindu_face ~ child_age_centered + language, 
  family="binomial", fl)

summary(label_face_hindu_glm)
label_face_hindu_glm_coefs <- cbind(round(exp(coef(label_face_hindu_glm)), 2),
round(exp(confint(label_face_hindu_glm)), 2))
```

```{r label-hindu-int-glm}
label_face_hindu_int_glm <- glm(
  hindu_face ~ child_age_centered*language, 
  family="binomial", fl)

label_face_hindu_int_glm_coefs <- cbind(round(exp(coef(label_face_hindu_int_glm)), 2),
round(exp(confint(label_face_hindu_int_glm)), 2))

Anova(label_face_hindu_int_glm)
```
We saw significant effects of language ($`r reportAnova(label_face_hindu_int_glm, "language")`$), child age ($`r reportAnova(label_face_hindu_int_glm, "child_age_centered")`$), and their interaction ($`r reportAnova(label_face_hindu_int_glm, "child_age_centered:language")`$).
Children robustly selected the hindu face as a speaker of Gujarati (58\% of trials; $`r reportORs(label_face_hindu_int_glm_coefs, "(Intercept)")`$), and did so significantly less for Mandarin (2\% of trials; $`r reportORs(label_face_hindu_int_glm_coefs, "languageMandarin")`$), 
English (2\% of trials; $`r reportORs(label_face_hindu_int_glm_coefs, "languageEnglish")`$), 
Urdu (7\% of trials; $`r reportORs(label_face_hindu_int_glm_coefs, "languageUrdu")`$), 
Tamil (25\% of trials; $`r reportORs(label_face_hindu_int_glm_coefs, "languageTamil")`$), 
Hindi (35\% of trials; $`r reportORs(label_face_hindu_int_glm_coefs, "languageHindi")`$), and 
Marathi (49\% of trials; $`r reportORs(label_face_hindu_int_glm_coefs, "languageMarathi")`$).
With age, children became less likely to select the hindu face as the speaker of 
Urdu (from 15\% to 2\%; $`r reportORs(label_face_hindu_int_glm_coefs, "child_age_centered:languageUrdu")`$), 
Chinese (from 2\% to 1\%; $`r reportORs(label_face_hindu_int_glm_coefs, "child_age_centered:languageMandarin")`$), and 
Tamil (from 31\% to 22\%; $`r reportORs(label_face_hindu_int_glm_coefs, "child_age_centered:languageTamil")`$).

#### Muslim face (from language name)

```{r label-muslim-glm, include=F}
label_face_muslim_glm <- glm(
  muslim_face ~ child_age_centered + language, 
  family="binomial", fl)

cbind(round(exp(coef(label_face_muslim_glm)), 2),
round(exp(confint(label_face_muslim_glm)), 2)) 
```

```{r label-muslim-int-glm}
label_face_muslim_int_glm <- glm(
  muslim_face ~ child_age_centered*language, 
  family="binomial", fl)

label_face_muslim_int_glm_coefs <- cbind(round(exp(coef(label_face_muslim_int_glm)), 2),
round(exp(confint(label_face_muslim_int_glm)), 2)) 

Anova(label_face_muslim_int_glm)
```

We saw significant effects of language ($`r reportAnova(label_face_muslim_int_glm, "language")`$), child age ($`r reportAnova(label_face_muslim_int_glm, "child_age_centered")`$), and their interaction ($`r reportAnova(label_face_muslim_int_glm, "child_age_centered:language")`$): with age, children became increasingly likely to select the \textsc{muslim} face as the speaker of Urdu (from 58\% of trials in 3rd grade to 93\% of trials in 7th; $`r reportORs(label_face_muslim_int_glm_coefs, "languageUrdu")`$).

#### Dravidian face (from language name)

```{r label-dravidian-glm, include=F}
label_face_dravidian_glm <- glm(
  dravidian_face ~ child_age_centered + language, 
  family="binomial", fl)

cbind(round(exp(coef(label_face_dravidian_glm)), 2),
round(exp(confint(label_face_dravidian_glm)), 2))
```

```{r label-dravidian-int-glm}
label_face_dravidian_int_glm <- glm(
  dravidian_face ~ child_age_centered*language, 
  family="binomial", fl)

label_face_dravidian_int_glm_coefs <- cbind(round(exp(coef(label_face_dravidian_int_glm)), 2),
round(exp(confint(label_face_dravidian_int_glm)), 2))

Anova(label_face_dravidian_int_glm)
```

We saw significant effects of language ($`r reportAnova(label_face_dravidian_int_glm, "language")`$), such that children preferred the dravidian faces as speakers of Tamil (53\% of trials overall; $`r reportORs(label_face_dravidian_int_glm_coefs, "languageTamil")`$) and Marathi (38\% of trials; $`r reportORs(label_face_dravidian_int_glm_coefs, "languageMarathi")`$), and significantly less for English (2\% of trials; $`r reportORs(label_face_dravidian_int_glm_coefs, "languageEnglish")`$), Mandarin (4\% of trials; $`r reportORs(label_face_dravidian_int_glm_coefs, "languageMandarin")`$), Urdu (7\% of trials; $`r reportORs(label_face_dravidian_int_glm_coefs, "languageUrdu")`$), Gujarati (21\% of trials; $`r reportORs(label_face_dravidian_int_glm_coefs, "(Intercept)")`$), and Hindi (10\% of trials; $`r reportORs(label_face_dravidian_int_glm_coefs, "languageEnglish")`$).  
A significant interaction between language and child age ($`r reportAnova(label_face_dravidian_int_glm, "child_age_centered:language")`$) additionally suggested that, with age, children became more likely to identify the dravidian face as specifically a potential speaker of Tamil (from 33\% of trials in 3rd grade, to 68\% of trials in 7th grade; $`r reportORs(label_face_dravidian_int_glm_coefs, "child_age_centered:languageTamil")`$). 

* This reflects accurate model of language--phenotype association

#### East Asian face (from language name)

```{r label-asian-glm, include=F}
label_face_asian_glm <- glm(
  asian_face ~ child_age_centered + language, 
  family="binomial", fl)

cbind(round(exp(coef(label_face_asian_glm)), 2),
round(exp(confint(label_face_asian_glm)), 2)) 
```

```{r label-asian-int-glm}
label_face_asian_int_glm <- glm(
  asian_face ~ child_age_centered*language, 
  family="binomial", fl)

label_face_asian_int_glm_coefs <- cbind(round(exp(coef(label_face_asian_int_glm)), 2),
round(exp(confint(label_face_asian_int_glm)), 2))

Anova(label_face_asian_int_glm)
```

We saw a significant effect of language ($`r reportAnova(label_face_asian_int_glm, "language")`$) and its interaction with child age ($`r reportAnova(label_face_asian_int_glm, "child_age_centered:language")`$) such that children were most likely to select the asian face in response to Chinese (85\% across trials; $`r reportORs(label_face_asian_int_glm_coefs, "languageMandarin")`$) or English (9\%; $`r reportORs(label_face_asian_int_glm_coefs, "languageEnglish")`$), and avoided it in response to Gujarati (4\% across trials; $`r reportORs(label_face_asian_int_glm_coefs, "(Intercept)")`$) --- tendencies that persisted or strengthened over time. That is, with age, children became even less likely to identify the asian face as a speaker of Gujarati (10\% to 1\%; $`r reportORs(label_face_asian_int_glm_coefs, "child_age_centered")`$), and all the more likely to identify the asian face as a speaker of Chinese (from 73\% in 3rd grade to 96\% in 7th; $`r reportORs(label_face_asian_int_glm_coefs, "child_age_centered:languageMandarin")`$) or English (14\% to 12\%; $`r reportORs(label_face_asian_int_glm_coefs, "child_age_centered:languageEnglish")`$).

#### White face (from language name)

```{r label-white-glm, include=F}
label_face_white_glm <- glm(
  white_face ~ child_age_centered + language, 
  family="binomial", fl)

cbind(round(exp(coef(label_face_white_glm)), 2),
round(exp(confint(label_face_white_glm)), 2)) 
```

```{r label-white-int-glm}
options(scipen=10000)
label_face_white_int_glm <- glm(
  white_face ~ child_age_centered*language, 
  family="binomial", fl)

label_face_white_int_glm_coefs <- cbind(round(exp(coef(label_face_white_int_glm)), 2),
round(exp(confint(label_face_white_int_glm)), 2))

Anova(label_face_white_int_glm)
```

We saw significant effects of language ($`r reportAnova(label_face_white_int_glm, "language")`$), child age ($`r reportAnova(label_face_white_int_glm, "child_age_centered")`$), and their interaction ($`r reportAnova(label_face_white_int_glm, "child_age_centered:language")`$), such that children showed a preference for the white face when asked about English (83\% of all trials; $`r reportORs(label_face_white_int_glm_coefs, "languageEnglish")`$), Chinese (8\% of all trials; $`r reportORs(label_face_white_int_glm_coefs, "languageMandarin")`$), and Tamil (9\% of all trials; $`r reportORs(label_face_white_int_glm_coefs, "languageTamil")`$), and a dispreference when asked about Gujarati (3\% of all trials; $`r reportORs(label_face_white_int_glm_coefs, "(Intercept)")`$). 
With age, children became even more likely to select the white face in response to English (from 73\% in 3rd grade to 92\% in 7th grade; $`r reportORs(label_face_white_int_glm_coefs, "child_age_centered:languageEnglish")`$) and less likely to select the white face in response to Gujarati (6\% down to 1\%; $`r reportORs(label_face_white_int_glm_coefs, "child_age_centered")`$).


# Mixed Effects Multinomial Regression  
## AUDIO  
```{r fa-mblogit, warning=F}
# dropping idks and multiple selections
fa_for_plots <- fa %>% filter(face!="idk",
                              num_faces==1)
fa_for_plots$age <- fa_for_plots$child_age_centered
fa_for_plots$face <- as.factor(fa_for_plots$face) 
fa_for_plots$face <- relevel(fa_for_plots$face, ref="hindu")

fa_mod <- mblogit(face ~ 0+language*age,
                   random=~1|id,
                   data = fa_for_plots)
summary(fa_mod)
```

```{r fa-mblogit-plot}
sjPlot::plot_model(fa_mod) +
  theme_blank() +
  theme(strip.text = element_text(color="gray30", size=12, face="bold")) +
 # theme(panel.grid.major.y=element_line(color="gray80")) +
  geom_hline(yintercept=1, lty=2, color="gray50") +
  scale_color_manual(values=c("#fc8d59", "#99d594")) +
  labs(title="Face Selection: Who could be speaking?")

# empty if CI crosses 1, otherwise colored according to polarity

ggsave("fa_mod_with_age_interaction.png", device = "png", 
       path = "plots/forest_plots/",
       scale = 1, width = 7, height = 6, units = "in")
```

```{r famod-table}
sjPlot::tab_model(fa_mod)
```

```{r fa-id-mblogit, warning=F}
i <- read.csv(here('data/language_identification_correct.csv'))

fai <- merge(fa_for_plots, i, by=c("language", "id"))

# dropping idks and multiple selections
fai_mod <- mblogit(face ~ language*id_correct + age,
                   #random=~1|id,
                   data = fai)
summary(fai_mod)
```

```{r fa-mblogit-id-plot}

sjPlot::plot_model(fai_mod) +
  theme_blank() +
  theme(strip.text = element_text(color="gray30", size=12, face="bold")) +
 # theme(panel.grid.major.y=element_line(color="gray80")) +
  geom_hline(yintercept=1, lty=2, color="gray50") +
  scale_color_manual(values=c("#fc8d59", "#99d594")) +
  labs(title="Face Selection: Who could be speaking?")

ggsave("fa_mod_with_id_interaction.png", device = "png", 
       path = "plots/forest_plots/",
       scale = 1, width = 7, height = 6, units = "in")
```

```{r famod-id-table}
sjPlot::tab_model(fai_mod)
```

```{r fa-idint-mblogit}
# dropping idks and multiple selections
faint_mod <- mblogit(face ~ language*id_correct*child_age_centered,
                   #random=~1|id,
                   data = fai[fai$face!="idk" & fai$num_faces==1,])
summary(faint_mod)
```

## LABEL

```{r fl-mblogit, warning=F}
# dropping idks and multiple selections
fl_for_plots <- fl %>% filter(face!="idk",
                              num_faces==1)
fl_for_plots$age <- fl_for_plots$child_age_centered
fl_for_plots$face <- as.factor(fl_for_plots$face) 
fl_for_plots$face <- relevel(fl_for_plots$face, ref="hindu")

fl_mod <- mblogit(face ~ language*age,
                   random=~1|id,
                   data = fl_for_plots)
summary(fl_mod)
```

```{r fl-mblogit-plot}
sjPlot::plot_model(fl_mod) +
  theme_blank() +
  theme(strip.text = element_text(color="gray30", size=12, face="bold")) +
 # theme(panel.grid.major.y=element_line(color="gray80")) +
  geom_hline(yintercept=1, lty=2, color="gray50") +
  scale_color_manual(values=c("#fc8d59", "#99d594")) +
  labs(title="Face Selection: Who speaks [LANGUAGE}?")

ggsave("fl_mod_with_age_interaction.png", device = "png", 
       path = "plots/forest_plots/",
       scale = 1, width = 7, height = 6, units = "in")
```

```{r flmod-table}
sjPlot::tab_model(fl_mod)
```

```{r fl-id-mblogit, warning=F}
i <- read.csv(here('data/language_identification_correct.csv'))

fli <- merge(fl_for_plots, i, by=c("language", "id"))

# dropping idks and multiple selections
fli_mod <- mblogit(face ~ language*id_correct + age,
                   #random=~1|id,
                   data = fli)
summary(fli_mod)
```

```{r fl-mblogit-id-plot}
sjPlot::plot_model(fli_mod) +
  theme_blank() +
  theme(strip.text = element_text(color="gray30", size=12, face="bold")) +
  geom_hline(yintercept=1, lty=2, color="gray50") +
  scale_color_manual(values=c("#fc8d59", "#99d594")) +
  labs(title="Face Selection: Who speaks [LANGUAGE}?")

ggsave("fl_mod_with_id_interaction.png", device = "png", 
       path = "plots/forest_plots/",
       scale = 1, width = 7, height = 6, units = "in")
```

```{r relmod-id-table}
sjPlot::tab_model(fli_mod)
```

```{r fl-idint-mblogit, warning=F}
flint_mod <- mblogit(face ~ language*id_correct*age,
                   #random=~1|id,
                   data = fli)
summary(flint_mod)
```

## BOTH   
```{r f-presentation-mblogit, warning=F}
f_for_plots <- f %>% filter(face!="idk",
                            num_faces==1)
f_for_plots$age <- f_for_plots$child_age_centered                            
fi <- merge(f_for_plots, i, by=c("language", "id"))
finoeng_df <- fi %>% filter(army_navy_language!="english")

f_present_mod <- mblogit(face ~ language*presentation + age,
                   #random=~1|id,
                   data = finoeng_df)

summary(f_present_mod)
```

```{r f-presentation-mblogit-plot}
sjPlot::plot_model(f_present_mod) +
  theme_blank() +
  theme(strip.text = element_text(color="gray30", size=12, face="bold")) +
 # theme(panel.grid.major.y=element_line(color="gray80")) +
  geom_hline(yintercept=1, lty=2, color="gray50") +
  scale_color_manual(values=c("#fc8d59", "#99d594")) +
  labs(title="Face Selection")

ggsave("f_presentation_mod_just_age.png", device = "png", 
       path = "plots/forest_plots/",
       scale = 1, width = 7, height = 6, units = "in")
```

```{r f-presentation-mod-table}
sjPlot::tab_model(f_present_mod)
```

```{r f-presentation-ageint-mblogit}
f_present_ageint_mod <- mblogit(face ~ language*presentation*age,
                   #random=~1|id,
                   data = finoeng_df)

summary(f_present_ageint_mod)

anova(f_present_mod, f_present_ageint_mod)
```

```{r f-presentation-ageint-mblogit-plot}
sjPlot::plot_model(f_present_ageint_mod) +
  theme_blank() +
  theme(strip.text = element_text(color="gray30", size=12, face="bold")) +
 # theme(panel.grid.major.y=element_line(color="gray80")) +
  geom_hline(yintercept=1, lty=2, color="gray50") +
  scale_color_manual(values=c("#fc8d59", "#99d594")) +
  labs(title="Face Selection")

ggsave("f_presentation_mod_with_age_interaction.png", device = "png", 
       path = "plots/forest_plots/",
       scale = 1, width = 7, height = 6, units = "in")
```

```{r f-presentation-ageint-table}
sjPlot::tab_model(f_present_ageint_mod)
```
