---
title: "India Sociolinguistics Religion Associations Analyses"
author: "Ruthe Foushee"
date: "2023-08-18"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r religion-setup, include=FALSE}
library(here)
here::i_am('1_speaker-associations/1b_religion.Rmd')

knitr::opts_chunk$set(
  echo = FALSE, message=F, warning=F,
  fig.width = 6)

source(here('isl-resources.R'))
```

```{r read-in-data}
a <- read.csv(here('data/r_dfs/associations_data.csv'))[,-1]

factor_vars <- c('study_name', 'id', 'child_sex', 'child_religion', 
                 'school', 'standard',
                 'question_type', 'language', 'speaker_gender', 
                 'origin', 'geographic_origin', 'religion', 'wealth',
                 'army_navy_language')

numeric_vars <- c('standard_num', 'child_age', 'child_age_centered', 
                  'sequence', 'coded_wealth')

a <- a %>%
  mutate_at(factor_vars, as.factor) %>%
  mutate_at(numeric_vars, as.numeric)

r <- a %>%
  filter(religion!="")
```

```{r religion-no-opinion-trials}
N_TRIALS <- r %>%
  filter(no_opinion_religion==1) %>%
  summarize(no_opinion_trials=n()) %>%
  as.numeric()

N_CHILDREN <- r %>%
  filter(no_opinion_religion==1) %>%
  group_by(id) %>%
  summarize(no_opinion_trials=n()) %>%
  summarize(n_children=n()) %>%
  as.numeric()
  
r %>%
  filter(no_opinion_religion==1) %>%
  group_by(id)%>%
  summarize(no_opinion_trials=n()) %>%
  group_by(no_opinion_trials) %>%
  summarize(n_children=n()) %>%
  kable(.)

r %>%
  filter(no_opinion_religion==1) %>%
  group_by(language)%>%
  summarize(n=n()) %>%
  arrange(desc(n)) %>%
  kable(.)

# 273 trials opted out, 84 children, most for chinese (88)
```

"No opinion" selected on `r N_TRIALS` trials by `r N_CHILDREN` children; all but 3 children selected single response.

```{r religion-single-trials}
# 3 trials chose more than one, 
table(r$religion)

r[r$religion=="hindu muslim",]$id #Z07A06, Z03C18

r[r$religion=="jain buddhist",]$id #Z07A06
```

Multiple religions selected on three trials ("hindu and muslim" twice in response to audio clips of spoken Urdu; "jain and buddhist" once in response to an audio clip of spoken Tamil)

```{r religion-overall-barplot, include=F}
religion_summary_tab <- r %>%
  ungroup(.) %>%
  dplyr::select("language", all_of(religion_vars)) %>%
  gather(., religion, selection, -language) %>%
    group_by(language, religion) %>%
    summarize(mean=na.mean(selection),
              cilo = mean-ci.low(selection),
              cihi = mean+ci.high(selection)) 

religion_summary_tab$religion <- factor(
  religion_summary_tab$religion, 
  levels=religion_vars, 
  labels=religion_labels)

ggplot(religion_summary_tab, 
       aes(x=religion, y=mean, fill=religion)) +
    geom_bar(stat="identity") + 
    geom_errorbar(aes(ymin=cilo, ymax=cihi), width=0, 
                  color=line_color) + 
    facet_wrap(~language, ncol=2) +
    scale_fill_manual(values = religion_colors,
                      religion_legend_title1) +
    ylim(0, 1) +
    sans_theme +
    theme(legend.title = element_text(
      size=10, colour="gray30", family="sans", face="italic")) +
    ylab("Mean")

ggsave("religious_associations.png", device = "png", 
       path = "plots/",
       scale = 1, width = 7, height = 6, units = "in")
```

## Over Time

### By Standard

```{r religion-std-lineplot}
religion_std_summary_tab <- r %>%
  ungroup(.) %>%
  dplyr::select("language", "standard", "standard_num",
    all_of(religion_vars)) %>%
  gather(., religion, selection, -language, -standard, -standard_num) %>%
    group_by(language, standard, standard_num, religion) %>%
    summarize(mean=na.mean(selection),
              cilo = mean-ci.low(selection),
              cihi = mean+ci.high(selection)) 

religion_std_summary_tab$religion <- factor(
  religion_std_summary_tab$religion, 
  levels=religion_vars, 
  labels=religion_labels)

ggplot(religion_std_summary_tab, 
       aes(x=standard_num, y=mean, color=religion)) +
    geom_line(aes(lty=religion)) + 
    geom_point(aes(shape=religion)) +
    geom_errorbar(aes(ymin=cilo, ymax=cihi), width=0) +
    facet_wrap(~language, ncol=4) +
    scale_color_manual(values=religion_colors, religion_legend_title) + 
    scale_shape_manual(values=religion_shapes, religion_legend_title) +
    scale_linetype_manual(values=religion_ltys,
                          religion_legend_title) +
    ylim(0, 1) +
    scale_x_continuous(breaks=c(1, 2, 3), 
                       label=std_axis_labels) +
   # labs(title="religion Associations Across Standards 3-7") +
    sans_axes_theme +
    theme(legend.position = "bottom") +
    xlab("Grade") +
    ylab("Mean")
  
ggsave("religion_std.png", device = "png", 
       path = "plots/final/",
       scale = 1, width = 7, height = 5, units = "in")
```

```{r religion-std-barplot, include=F}

ggplot(religion_std_summary_tab, 
       aes(x=religion, y=mean, fill=religion)) +
    geom_bar(stat="identity") + 
    geom_errorbar(aes(ymin=cilo, ymax=cihi), width=0, 
                  color=line_color) + 
    facet_wrap(~language + standard, ncol=3) +
    scale_fill_manual(values = religion_colors, religion_legend_title1) +
    ylim(0, 1) +
    xlab("Grade") +
    ylab("Mean") +
    sans_axes_theme +
    theme(legend.title = element_text(
      size=10, colour="gray30", family="sans", face="italic"))

ggsave("plots/religion_religion_std_barplot.png", height=16, width=14, units="in")
```

### With Age. 

```{r religion-age, include=F}
religion_age_df <- r %>%
  ungroup(.) %>%
  dplyr::select(
    "language", "child_age", all_of(religion_vars)) %>%
  gather(., religion, selection, -language, -child_age) 

religion_age_df$religion <- factor(religion_age_df$religion, 
      levels=religion_vars, labels=religion_labels)

ggplot(religion_age_df, 
       aes(x=child_age, y=selection, color=religion, lty=religion, fill=religion)) +
    stat_smooth(aes(x=child_age, y=selection), 
                method="lm", level=.75, fullrange=T) +
    facet_wrap(~language, ncol=4) +
    scale_color_manual(values = religion_colors, religion_legend_title1) +
    scale_linetype_manual(values=religion_ltys, religion_legend_title1) +
    scale_fill_manual(values=religion_colors, religion_legend_title1) +
    ylim(0, 1) +
    ylab("Mean") +
    xlab("Child Age (yrs)") +
    #labs(title="religion Associations with Age") +
    sans_axes_theme +
    theme(legend.title = element_text(
      size=10, colour="gray30", family="sans", face="italic"))

ggsave("religion_age_lm.png", device = "png", 
       path = "plots/",
       scale = 1, width = 7, height = 6, units = "in")
```

## Models: Odds of Religion Selection

#### Hindu

```{r hindu-glm, include=F}
ass_hindu_glm <- glm(
  hindu ~ child_age + language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_hindu_glm)), 2),
round(exp(confint(ass_hindu_glm)), 2))%>%
  kable(.)
```

```{r hindu-int-glm, include=F}
ass_hindu_int_glm <- glm(
  hindu ~ child_age*language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_hindu_int_glm)), 2),
round(exp(confint(ass_hindu_int_glm)), 2))%>%
  kable(.)

summary(ass_hindu_int_glm)

Anova(ass_hindu_int_glm)
```

```{r hindu-2int-glm}
ass_hindu_2int_glm <- glm(
  hindu ~ child_age*language + child_religion*language, 
  family="binomial", a[a$child_religion!="other",])

cbind(round(exp(coef(ass_hindu_2int_glm)), 2),
round(exp(confint(ass_hindu_2int_glm)), 2))%>%
  kable(.)

summary(ass_hindu_2int_glm)

Anova(ass_hindu_2int_glm)
```

#### Muslim

```{r muslim-glm,include=F}
ass_muslim_glm <- glm(
  muslim ~ child_age + language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_muslim_glm)), 2),
round(exp(confint(ass_muslim_glm)), 2))%>%
  kable(.)
```

```{r muslim-int-glm, include=F}
ass_muslim_int_glm <- glm(
  muslim ~ child_age*language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_muslim_int_glm)), 2),
round(exp(confint(ass_muslim_int_glm)), 2))%>%
  kable(.)

summary(ass_muslim_int_glm)

Anova(ass_muslim_int_glm)
```

```{r muslim-1int-glm}
ass_muslim_1int_glm <- glm(
  muslim ~ child_age + child_religion*language, 
  family="binomial", a[a$child_religion!="other",])

cbind(round(exp(coef(ass_muslim_1int_glm)), 2),
round(exp(confint(ass_muslim_1int_glm)), 2))%>%
  kable(.)

summary(ass_muslim_1int_glm)

Anova(ass_muslim_1int_glm)
```

#### Jain

```{r jain-glm, include=F}
ass_jain_glm <- glm(
  jain ~ child_age + language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_jain_glm)), 2),
round(exp(confint(ass_jain_glm)), 2))%>%
  kable(.)
```

```{r jain-int-glm, include=F}
ass_jain_int_glm <- glm(
  jain ~ child_age*language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_jain_int_glm)), 2),
round(exp(confint(ass_jain_int_glm)), 2))%>%
  kable(.)

summary(ass_jain_int_glm)

Anova(ass_jain_int_glm)
```

```{r jain-1int-glm}
ass_jain_1int_glm <- glm(
  jain ~ child_age + child_religion*language, 
  family="binomial", a[a$child_religion!="other",])

ass_jain_1int_glm_coefs <- 
  as.data.frame(cbind(round(exp(coef(ass_jain_1int_glm)), 2),
round(exp(confint(ass_jain_1int_glm)), 2)))

ass_jain_1int_glm_coefs$toss <- ass_jain_1int_glm_coefs$`2.5 %`<1 & ass_jain_1int_glm_coefs$`97.5 %`>1

ass_jain_1int_glm_coefs %>%filter(toss==0)

summary(ass_jain_1int_glm)

Anova(ass_jain_1int_glm)
```

#### Christian

```{r christian-glm, include=F}
ass_christian_glm <- glm(
  christian ~ child_age + language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_christian_glm)), 2),
round(exp(confint(ass_christian_glm)), 2))%>%
  kable(.)
```

```{r christian-int-glm, include=F}
ass_christian_int_glm <- glm(
  christian ~ child_age*language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_christian_int_glm)), 2),
round(exp(confint(ass_christian_int_glm)), 2))%>%
  kable(.)

summary(ass_christian_int_glm)

options(scipen=100)

Anova(ass_christian_int_glm)
```

```{r christian-2int-glm}
ass_christian_2int_glm <- glm(
  christian ~ child_age*language + child_religion*language, 
  family="binomial", r[r$child_religion!="other",])

ass_christian_2int_glm_coefs <- 
  as.data.frame(cbind(round(exp(coef(ass_christian_2int_glm)), 2),
                      round(exp(confint(ass_christian_2int_glm)), 2)))
ass_christian_2int_glm_coefs$toss <- ass_christian_2int_glm_coefs$`2.5 %`<1 & ass_christian_2int_glm_coefs$`97.5 %`>1

ass_christian_2int_glm_coefs %>%filter(toss==0)

summary(ass_christian_2int_glm)

options(scipen=100)

Anova(ass_christian_2int_glm)
```

#### Buddhist

```{r buddhist-glm, include=F}
ass_buddhist_glm <- glm(
  buddhist ~ child_age + language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_buddhist_glm)), 2),
round(exp(confint(ass_buddhist_glm)), 2))%>%
  kable(.)
```

```{r buddhist-int-glm, include=F}
ass_buddhist_int_glm <- glm(
  buddhist ~ child_age*language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_buddhist_int_glm)), 2),
round(exp(confint(ass_buddhist_int_glm)), 2))%>%
  kable(.)

summary(ass_buddhist_int_glm)

Anova(ass_buddhist_int_glm)
```

```{r buddhist-2int-glm}
ass_buddhist_2int_glm <- glm(
  buddhist ~ child_age*language + child_religion*language, 
  family="binomial", r[r$child_religion!="other",])

ass_buddhist_2int_glm_coefs <- 
  as.data.frame(cbind(round(exp(coef(ass_buddhist_2int_glm)), 2),
round(exp(confint(ass_buddhist_2int_glm)), 2)))

ass_buddhist_2int_glm_coefs$toss <- ass_buddhist_2int_glm_coefs$`2.5 %`<1 & ass_buddhist_2int_glm_coefs$`97.5 %`>1

ass_buddhist_2int_glm_coefs %>% filter(toss==0)

summary(ass_buddhist_2int_glm)

Anova(ass_buddhist_2int_glm)
```

### No Opinion 

```{r}
ass_idk_glm <- glm(
  no_opinion_religion ~ child_age + language, 
  family="binomial", r[r$child_religion!="other",])

ass_idk_glm_coefs <- 
  as.data.frame(cbind(round(exp(coef(ass_idk_glm)), 2),
round(exp(confint(ass_idk_glm)), 2)))

ass_idk_glm_coefs$toss <- ass_idk_glm_coefs$`2.5 %`<1 & ass_idk_glm_coefs$`97.5 %`>1

ass_idk_glm_coefs %>% filter(toss==0)

summary(ass_buddhist_2int_glm)

Anova(ass_buddhist_2int_glm)
```


## Mixed Effects Multinomial Regression  

```{r rel-mblogit, warning=F}
r_for_plots <- r %>% filter(religion!="",
                            religion!="idk",
                            religion %in% religion_vars)
r_for_plots$religion <- relevel(r_for_plots$religion, ref="hindu")
r_for_plots$age <- r_for_plots$child_age_centered
r_for_plots$religion_labeled <- plyr::mapvalues(r_for_plots$religion,
                                             from=religion_vars[1:5],
                                             to=religion_labels[1:5])


# dropping idks
rel_mod <- mblogit(religion_labeled ~ language*age,
                   random=~1|id,
                   data = r_for_plots)
summary(rel_mod)
```
```{r rel-mblogit-plot}
sjPlot::plot_model(rel_mod) +
  theme_blank() +
  theme(strip.text = element_text(color="gray30", size=12, face="bold")) +
 # theme(panel.grid.major.y=element_line(color="gray80")) +
  geom_hline(yintercept=1, lty=2, color="gray50") +
  scale_color_manual(values=c("#fc8d59", "#99d594")) +
  labs(title="Religion: This speaker is...")

ggsave("rel_mod_with_age_interaction.png", device = "png", 
       path = "plots/forest_plots/",
       scale = 1, width = 7, height = 6, units = "in")
```

```{r relmod-table}
sjPlot::tab_model(rel_mod)
```

```{r rel-mblogit-simple-plot, warning=F}
rel_mod_no_int <- mblogit(religion_labeled ~ language + age,
                   random=~1|id,
                   r_for_plots) # dropping idks

sjPlot::plot_model(rel_mod_no_int) +
  theme_blank() +
  theme(strip.text = element_text(color="gray30", size=12, face="bold")) +
 # theme(panel.grid.major.y=element_line(color="gray80")) +
  geom_hline(yintercept=1, lty=2, color="gray50") +
  scale_color_manual(values=c("#fc8d59", "#99d594")) +
  labs(title="Religion: This speaker is...")

ggsave("rel_mod_just_age.png", device = "png", 
       path = "plots/forest_plots/",
       scale = 1, width = 7, height = 6, units = "in")
```

```{r rel-ida-mblogit, warning=F}
i <- read.csv(here('data/language_identification_correct.csv'))

ri <- merge(r_for_plots, i, by=c("language", "id"))

rel_id_mod <- mblogit(religion_labeled ~ language*id_correct + age,
                   random=~1|id,
                   data = ri)
summary(rel_id_mod)
```

```{r rel-mblogit-id-plot}

sjPlot::plot_model(rel_id_mod) +
  theme_blank() +
  theme(strip.text = element_text(color="gray30", size=12, face="bold")) +
 # theme(panel.grid.major.y=element_line(color="gray80")) +
  geom_hline(yintercept=1, lty=2, color="gray50") +
  scale_color_manual(values=c("#fc8d59", "#99d594")) +
  labs(title="Religion: This speaker is...")

ggsave("rel_mod_with_id_interaction.png", device = "png", 
       path = "plots/forest_plots/",
       scale = 1, width = 7, height = 6, units = "in")
```

```{r relmod-id-table}
sjPlot::tab_model(rel_id_mod)
```

```{r rel-idaint-mblogit, warning=F}
rel_idint_mod <- mblogit(religion_labeled ~ language*id_correct*age,
                   random=~1|id,
                   data = ri)
summary(rel_idint_mod)
```