---
title: "India Sociolinguistics Geographic Associations Analyses"
author: "Ruthe Foushee"
date: "2023-08-18"
output:
  pdf_document: default
  html_document:
    df_print: paged
header-includes:
- \usepackage{array}
- \usepackage{longtable}
- \newcommand\textstyleStrongEmphasis[1]{\textbf{#1}}
- \makeatletter
- \newcommand\arraybslash{\let\\\@arraycr}
---

```{r origin-setup, include=FALSE}
library(here)
here::i_am('2_speaker-associations/2a_geographic-origin.Rmd')

knitr::opts_chunk$set(
  echo = FALSE, message=F, warning=F,
  fig.width = 6)

source(here('isl-resources.R'))
```

```{r read-in-data}
a <- read.csv(here('data/r_dfs/subsets/associations_data.csv'))[,-1]

factor_vars <- c('study_name', 'id', 'child_sex', 'child_religion', 
                 'school', 'standard',
                 'question_type', 'language', 'speaker_gender', 
                 'origin', 'geographic_origin', 'religion', 'wealth',
                 'army_navy_language')

numeric_vars <- c('standard_num', 'child_age', 'child_age_centered', 
                  'sequence', 'coded_wealth')

a <- a %>%
  mutate_at(factor_vars, as.factor) %>%
  mutate_at(numeric_vars, as.numeric)

g <- a %>%
  filter(origin!="")
```

```{r origin-no-opinion-trials}
N_TRIALS <- g %>%
  filter(no_opinion_geo==1) %>%
  summarize(no_opinion_trials=n()) %>%
  as.numeric()

N_CHILDREN <- g %>%
  filter(no_opinion_geo==1) %>%
  group_by(id) %>%
  summarize(no_opinion_trials=n()) %>%
  summarize(n_children=n()) %>%
  as.numeric()
  
g %>%
  filter(no_opinion_geo==1) %>%
  group_by(id)%>%
  summarize(no_opinion_trials=n()) %>%
  group_by(no_opinion_trials) %>%
  summarize(n_children=n()) %>%
  kable(.)

g %>%
  filter(no_opinion_geo==1) %>%
  group_by(language)%>%
  summarize(n=n()) %>%
  arrange(desc(n)) %>%
  kable(.)

# 39 trials opted out from 27 children, most for chinese/tamil
```

"No opinion" selected on `r N_TRIALS` trials by `r N_CHILDREN` children; all children selected single response.

```{r origin-overall-barplot, include=F}
geographic_summary_tab <- g %>%
  ungroup(.) %>%
  dplyr::select("language", all_of(origin_vars)) %>%
  gather(., origin, selection, -language) %>%
    group_by(language, origin) %>%
    summarize(mean=na.mean(selection),
              cilo = mean-ci.low(selection),
              cihi = mean+ci.high(selection)) %>%
  mutate_at("language", order_languages)

geographic_summary_tab$var_labeled <- 
  factor(geographic_summary_tab$origin, 
  levels=origin_vars, 
  labels=origin_labels)

make_overall_barplot(geographic_summary_tab, origin_colors, 
                     "This speaker is from...") %>%
save_plot(., "barplot_overall", "geographic_associations")
```

## By Standard

```{r origin-std-lineplot}
geographic_std_summary_tab <- g %>%
  ungroup(.) %>%
  dplyr::select("language", "standard", "standard_num",
    all_of(origin_vars)) %>%
  gather(., origin, selection, -language, -standard, -standard_num) %>%
    group_by(language, standard, standard_num, origin) %>%
    summarize(mean=na.mean(selection),
              cilo = mean-ci.low(selection),
              cihi = mean+ci.high(selection)) %>%
  mutate_at("language", order_languages)

geographic_std_summary_tab$var_labeled <- factor(
  geographic_std_summary_tab$origin, 
  levels=origin_vars, 
  labels=origin_labels)

make_lineplot_by_std(geographic_std_summary_tab, 
                     origin_colors, origin_shapes, origin_ltys) %>%
save_plot(., which_data="geographic_origin", plot_class="line_std")
```

```{r origin-std-barplot, include=F}
make_barplot_by_std(geographic_std_summary_tab, origin_colors) %>%
  save_plot(., "barplot_std", "geographic_origin")
```

## With Age

```{r origin-age, include=F}
geographic_age_df <- g %>%
  ungroup(.) %>%
  dplyr::select(
    "language", "child_age_centered", all_of(origin_vars)) %>%
  gather(., origin, selection, -language, -child_age_centered) %>%
  mutate_at("language", order_languages)
geographic_age_df$var_labeled <- factor(geographic_age_df$origin, 
      levels=origin_vars, labels=origin_labels)

make_age_lm_plot(geographic_age_df, origin_colors, origin_ltys)

save_plot(which_data="geographic_origin", plot_class="age_lm")
```

## Mixed Effects Multinomial Regression  

### Language x Age
```{r geo-for-plots-data}
 # dropping idks
g_for_plots <- g %>% filter(origin!="idk",
                           origin!="")
g_for_plots$origin <- factor(g_for_plots$origin, levels=c("Gujarat",
                                                          "India",
                                                          "foreign"))
g_for_plots$var_labeled <- plyr::mapvalues(g_for_plots$origin,
                                             from=c("Gujarat",
                                                    "India",
                                                    "foreign"),
                                             to=c("Gujarat (same place as me)",
                                                  "another place in India",
                                                  "outside India (foreign)"))
g_for_plots$language <- order_languages(g_for_plots$language)
```

```{r geo-mblogit, warning=F}
geo_mod <- mblogit(var_labeled ~  0 + language*child_age_centered,
                   random=~1|id,
                   g_for_plots)

geo_noint_mod <- mblogit(var_labeled ~ 0 + language + child_age_centered,
                   random=~1|id,
                   g_for_plots)

anova(geo_noint_mod, geo_mod, test="Chisq") #language x age: X2(14)=67.9,p<0.001
```

There is a significant interaction between language and child age.

#### Forest Plot 

```{r geo-mblogit-plot}
gp <- make_forest_plot(geo_mod)
g_n <- get_point_sizes(g_for_plots, "Gujarat (same place as me)")
edited_gp <- edit_forest_plot_data(gp, g_n, 
                                   ordered_facet_levels = 
                                     c("another place in India",
                                       "outside India (foreign)"))
#edited_gp$data$facet <- paste(edited_gp$data$facet, "\nrelative to Gujarat", sep="")
updated_gp <- update_forest_plot(edited_gp, title="This speaker is from...")

save_forest_plot_svg(updated_gp, "geo_mod_with_age_interaction.svg")
save_forest_plot_png(updated_gp, "geo_mod_with_age_interaction.png")
```

#### Table  
```{r geomod-table}
prefix <- "geo"
filename <- paste(prefix, "_mod_tab.html", sep="")
file_path <- paste("tables/models/primary/", filename, sep="")
model <- geo_mod
sjPlot::tab_model(
      model, show.r2 = TRUE, show.icc = FALSE, show.re.var = FALSE, 
      p.style = "numeric_stars", emph.p = TRUE, 
      file = file_path)

geo_tab_df <- readHTMLTable(here(
  '2_speaker-associations/tables/models/primary/geo_mod_tab.html'), 
              header=T) 
geo_tab_df <- as.data.frame(geo_tab_df)
geo_tab_df_temp <- geo_tab_df
names(geo_tab_df) <- geo_tab_df[1,]
geo_tab_df <- geo_tab_df[-1,]
geo_tab_df$Predictors <- gsub("language", "", geo_tab_df$Predictors)
geo_tab_df$Predictors <- gsub("child_", "", geo_tab_df$Predictors)
geo_tab_df$Predictors <- gsub("_centered", "", geo_tab_df$Predictors)

another_place_in_india <- geo_tab_df[,1:4]
another_place_in_india$space <- ""

outside_india <- geo_tab_df[,5:7]

geo_mod_tab <- cbind(another_place_in_india, outside_india)

print.xtable(geo_mod_tab, type="latex", 
             file="tables/models/primary/geo_mod_tab.tex")
```

### Gender  

```{r geo-gender-mod}
g_for_plots$speaker_FEMALE <- plyr::mapvalues(g_for_plots$speaker_gender,
                                                    from=c("male", "female"),
                                                    to=c(0, 1))

g_for_plots$speaker_FEMALE <- factor(g_for_plots$speaker_FEMALE, levels=c(0, 1))

g_for_plots <- g_for_plots %>% filter(speaker_FEMALE!="")

geo_gender_mod <- mblogit(var_labeled ~ 0 + language*speaker_FEMALE + 
                            child_age_centered,
                          g_for_plots)

summary(geo_gender_mod)

#vif(geo_gender_mod)
```

```{r geo-gender-anova}
geo_gender_null_mod <- mblogit(var_labeled ~ 0 + language + speaker_FEMALE,
                   g_for_plots)

anova(geo_gender_null_mod, geo_gender_mod, test="Chisq") #X2(16)=33.8, p<0.01
```

#### Table  
```{r geo-gender-mod-tab}
#make_multinomial_html(geo_gender_mod, prefix="geo", model_class="gender")
prefix <- "geo"
filename <- paste(prefix, "_gender_mod_tab.html", sep="")
file_path <- paste("tables/models/gender/", filename, sep="")
model <- geo_gender_mod
sjPlot::tab_model(
      model, show.r2 = TRUE, show.icc = FALSE, show.re.var = FALSE, 
      p.style = "numeric_stars", emph.p = TRUE, 
      file = file_path)

geo_tab_df <- readHTMLTable(here(
  '2_speaker-associations/tables/models/gender/geo_gender_mod_tab.html'), 
              header=T) 
geo_tab_df <- as.data.frame(geo_tab_df)
geo_tab_df_temp <- geo_tab_df
names(geo_tab_df) <- geo_tab_df[1,]
geo_tab_df <- geo_tab_df[-1,]
geo_tab_df$Predictors <- gsub("language", "", geo_tab_df$Predictors)
geo_tab_df$Predictors <- gsub("child_", "", geo_tab_df$Predictors)
geo_tab_df$Predictors <- gsub("_centered", "", geo_tab_df$Predictors)

another_place_in_india <- geo_tab_df[,1:4]
another_place_in_india$space <- ""

outside_india <- geo_tab_df[,5:7]

geo_mod_tab <- cbind(another_place_in_india, outside_india)

print.xtable(geo_mod_tab, type="latex", 
             file="tables/models/gender/geo_gender_mod_tab.tex")
```

### Familiarity  
```{r geo-fam-rates}
gi %>%
  group_by(language, familiar) %>%
  summarize(n=n())
```

```{r geo-fam-mblogit, warning=F}
gi <- merge(g_for_plots, i, by=c("language", "id")) %>% 
  filter(!is.na(familiar),
         language!="Hindi",
         language!="English (India)",
         language!="Gujarati")

gi$language <- order_languages(gi$language)

geo_fam_mod <- mblogit(var_labeled ~ 0 + language*familiar +
                         child_age_centered, 
                       random=~1|id, data = gi)

geo_fam_mod_null <- mblogit(var_labeled ~ 0 + language + familiar + 
                              child_age_centered,
                   random=~1|id, data = gi)

anova(geo_fam_mod, geo_fam_mod_null, test="Chisq") #X2(8) = 29.7 p<0.001
```

#### Table  
```{r geomod-fam-table}
#make_multinomial_html(geo_fam_mod, prefix="geo", model_class="familiarity")
prefix <- "geo"
filename <- paste(prefix, "_fam_mod_tab.html", sep="")
file_path <- paste("tables/models/familiarity/", filename, sep="")
model <- geo_fam_mod
sjPlot::tab_model(
      model, show.r2 = TRUE, show.icc = FALSE, show.re.var = FALSE, 
      p.style = "numeric_stars", emph.p = TRUE, 
      file = file_path)

geo_tab_df <- readHTMLTable(here(
  '2_speaker-associations/tables/models/familiarity/geo_fam_mod_tab.html'), 
              header=T) 
geo_tab_df <- as.data.frame(geo_tab_df)
geo_tab_df_temp <- geo_tab_df
names(geo_tab_df) <- geo_tab_df[1,]
geo_tab_df <- geo_tab_df[-1,]
geo_tab_df$Predictors <- gsub("language", "", geo_tab_df$Predictors)
geo_tab_df$Predictors <- gsub("child_", "", geo_tab_df$Predictors)
geo_tab_df$Predictors <- gsub("_centered", "", geo_tab_df$Predictors)

another_place_in_india <- geo_tab_df[,1:4]
another_place_in_india$space <- ""

outside_india <- geo_tab_df[,5:7]

geo_mod_tab <- cbind(another_place_in_india, outside_india)

print.xtable(geo_mod_tab, type="latex", 
             file="tables/models/familiarity/geo_fam_mod_tab.tex")
```

## Combining Plots  

```{r geo-combined-labeled}
origin_legend_title <- "This speaker is from..."
origin_legend_title <- ""
origin_legend_labels <- c("Gujarat (same place as me)", 
                                "another place in India",
                                "outside India (foreign)",
                                "No opinion")

gs <- ggplot(geographic_std_summary_tab, 
       aes(x=standard_num, y=mean, color=var_labeled)) +
    geom_line(aes(lty=var_labeled), linewidth=1.1) + 
    geom_point(aes(shape=var_labeled)) +
    geom_errorbar(aes(ymin=cilo, ymax=cihi), width=0) +
    facet_wrap(~language, ncol=4) +
    scale_color_manual(values=origin_colors, origin_legend_title) + 
    scale_shape_manual(values=origin_shapes, origin_legend_title) +
    scale_linetype_manual(values=origin_ltys, origin_legend_title) +
    ylim(0, 1) +
    scale_x_continuous(breaks=c(3, 5, 7), label=std_axis_labels) +
    sans_axes_theme_bigger +
    theme(legend.position = "bottom",
          legend.key=element_rect(color=NA),
          legend.margin = margin(-5,0,0,0),
          strip.background = element_rect(color=line_color,linewidth = .75)) +
    xlab("Grade") +
    ylab("Mean Proportion")

final_gp <- updated_gp + theme(axis.text.y = element_text(face="bold", size=10),
                               axis.title.x=element_text(face="bold", size=10),
                               legend.title = element_text(face="bold"),
                               strip.text = element_text(color="gray30", 
                                                         size=11, 
                                                         face="bold.italic"),
          title=element_text(color="gray30", face="bold.italic", size=10),
          legend.key = element_rect(linewidth=0, color=NA),
          legend.text = element_text(color="gray30", size=10),
          axis.title.y=element_text(margin=margin(0,-10,0,0), face="bold"))#,
         # legend.margin = margin(0,0,0,-5))#,
         # panel.spacing.x = unit(0.3, "cm"))

cg <- ggarrange(gs, final_gp, labels='AUTO', 
                                           widths = c(4, 3), ncol = 2, nrow = 1, 
                                           align = 'v')
save_combined_plot_svg(
  ggarrange(gs, final_gp, labels='AUTO', widths = c(4, 3), 
            ncol = 2, nrow = 1, align = 'v'), "combined_geo_labeled.pdf"
  )

ggsave("combined_geo_labeled.svg", cg, path="plots/combined/",
       width = 190, scale=2, units ='mm')

save_combined_plot_svg(
  ggarrange(gs, final_gp, labels='AUTO', widths = c(4, 3), 
            ncol = 2, nrow = 1, align = 'v'), "combined_geo_labeled.svg"
  )
```

## Models

### Odds of Origin Selection

#### Gujarat (Same place as me)  

```{r gujarat-stats}
g %>% 
  mutate(total_trials=n(),
    n_trials=sum(origin=="Gujarat")) %>%
  distinct(id, .keep_all = T) %>%
  mutate(n_children=n(),
         prop = n_trials/total_trials) %>%
  distinct(n_trials, total_trials, prop, n_children)
```
`Gujarat' selected on 33\% of trials (606/1834), by 127 children.

```{r gujarat-glm}
ass_gujarat_glm <- glm(
  gujarat ~ child_age_centered + language, 
  family="binomial", g)

cbind(round(exp(coef(ass_gujarat_glm)), 2),
round(exp(confint(ass_gujarat_glm)), 2)) %>%
  kable(.)
```

```{r gujarat-int-glm}
ass_gujarat_int_glm <- glm(
  gujarat ~ child_age_centered*language, 
  family="binomial", g)

cbind(round(exp(coef(ass_gujarat_int_glm)), 2),
round(exp(confint(ass_gujarat_int_glm)), 2))%>%
  kable(.)

Anova(ass_gujarat_int_glm)
# sig interaction
```

```{r gujarat-id-glm}
ass_gujarat_id_glm <- glm(
  gujarat ~ language*id_correct + child_age_centered, 
  family="binomial", gi)

cbind(round(exp(coef(ass_gujarat_id_glm)), 2),
round(exp(confint(ass_gujarat_id_glm)), 2))%>%
  kable(.)

Anova(ass_gujarat_id_glm)
# sig interaction
```

#### Another part of India (A different city)  

```{r india-glm}
ass_india_glm <- glm(
  india ~ child_age_centered + language, 
  family="binomial", g)

cbind(round(exp(coef(ass_india_glm)), 2),
round(exp(confint(ass_india_glm)), 2))%>%
  kable(.)
```

```{r india-int-glm}
ass_india_int_glm <- glm(
  india ~ child_age_centered*language, 
  family="binomial", g)

cbind(round(exp(coef(ass_india_int_glm)), 2),
round(exp(confint(ass_india_int_glm)), 2))%>%
  kable(.)

Anova(ass_india_int_glm)
# n.s. interaction
```

#### Outside India (Foreign)  

```{r foreign-glm}
ass_foreign_glm <- glm(
  foreign ~ child_age_centered + language, 
  family="binomial", g)

cbind(round(exp(coef(ass_foreign_glm)), 2),
round(exp(confint(ass_foreign_glm)), 2))%>%
  kable(.)
```

```{r foreign-int-glm}
ass_foreign_int_glm <- glm(
  foreign ~ child_age_centered*language, 
  family="binomial", g)

cbind(round(exp(coef(ass_foreign_int_glm)), 2),
round(exp(confint(ass_foreign_int_glm)), 2))%>%
  kable(.)

Anova(ass_foreign_int_glm)
# sig interaction
```


```{r}
g_for_plots %>%
  group_by(id, language) %>%
  mutate(n=n()) %>%
  filter(n==2) %>%
  dplyr::select("id", "language", "speaker_gender", "origin", "n") %>%
  spread(speaker_gender, origin) %>%
  mutate(same_twice = female==male) %>%
  ungroup() %>%
  summarize(corr=sum(same_twice)/(sum(same_twice)+sum(same_twice==FALSE)))
```
```{r}
na.mean(g_for_plots$india) # 0.33
sd(g_for_plots$india) # 0.47

g_for_plots %>%
  group_by(language) %>%
  summarize(india_m=na.mean(india),
            india_sd = sd(india))
#3.06, 9.10, 7.26, 7.80 .21–.41

```
