---
title: "India Sociolinguistics Religion Associations Analyses"
author: "Ruthe Foushee"
date: "2023-08-18"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r religion-setup, include=FALSE}
library(here)
here::i_am('2_speaker-associations/2b_religion.Rmd')

knitr::opts_chunk$set(
  echo = FALSE, message=F, warning=F,
  fig.width = 6)

source(here('isl-resources.R'))
```

```{r read-in-data}
a <- read.csv(here('data/r_dfs/subsets/associations_data.csv'))[,-1]

factor_vars <- c('study_name', 'id', 'child_sex', 'child_religion', 
                 'school', 'standard',
                 'question_type', 'language', 'speaker_gender', 
                 'origin', 'geographic_origin', 'religion', 'wealth',
                 'army_navy_language')

numeric_vars <- c('standard_num', 'child_age', 'child_age_centered', 
                  'sequence', 'coded_wealth')

a <- a %>%
  mutate_at(factor_vars, as.factor) %>%
  mutate_at(numeric_vars, as.numeric)

r <- a %>%
  filter(religion!="")
```

```{r religion-no-opinion-trials}
N_TRIALS <- r %>%
  filter(no_opinion_religion==1) %>%
  summarize(no_opinion_trials=n()) %>%
  as.numeric()

N_CHILDREN <- r %>%
  filter(no_opinion_religion==1) %>%
  group_by(id) %>%
  summarize(no_opinion_trials=n()) %>%
  summarize(n_children=n()) %>%
  as.numeric()
  
r %>%
  filter(no_opinion_religion==1) %>%
  group_by(id)%>%
  summarize(no_opinion_trials=n()) %>%
  group_by(no_opinion_trials) %>%
  summarize(n_children=n()) %>%
  kable(.)

r %>%
  filter(no_opinion_religion==1) %>%
  group_by(language)%>%
  summarize(n=n()) %>%
  arrange(desc(n)) %>%
  kable(.)

# 273 trials opted out, 84 children, most for chinese (88)
```

"No opinion" selected on `r N_TRIALS` trials by `r N_CHILDREN` children; all but 3 children selected single response.

```{r religion-single-trials}
# 3 trials chose more than one, 
table(r$religion)

r[r$religion=="hindu muslim",]$id #Z07A06, Z03C18

r[r$religion=="jain buddhist",]$id #Z07A06
```

Multiple religions selected on three trials ("hindu and muslim" twice in response to audio clips of spoken Urdu; "jain and buddhist" once in response to an audio clip of spoken Tamil)

```{r religion-overall-barplot, include=F}
religion_summary_tab <- r %>%
  ungroup(.) %>%
  dplyr::select("language", all_of(religion_vars)) %>%
  gather(., religion, selection, -language) %>%
    group_by(language, religion) %>%
    summarize(mean=na.mean(selection),
              cilo = mean-ci.low(selection),
              cihi = mean+ci.high(selection)) 

religion_summary_tab$var_labeled <- factor(
  religion_summary_tab$religion, 
  levels=religion_vars, 
  labels=religion_labels)

make_overall_barplot(religion_summary_tab, religion_colors, 
                     "This speaker's religion is...") %>%
save_plot(., which_data="religious_associations", "barplot_overall")
```

## Over Time

### By Standard

```{r religion-std-lineplot}
religion_std_summary_tab <- r %>%
  ungroup(.) %>%
  dplyr::select("language", "standard", "standard_num",
    all_of(religion_vars)) %>%
  gather(., religion, selection, -language, -standard, -standard_num) %>%
    group_by(language, standard, standard_num, religion) %>%
    summarize(mean=na.mean(selection),
              cilo = mean-ci.low(selection),
              cihi = mean+ci.high(selection)) 

religion_std_summary_tab$var_labeled <- factor(
  religion_std_summary_tab$religion, 
  levels=religion_vars, 
  labels=religion_labels)

make_lineplot_by_std(religion_std_summary_tab, 
                     religion_colors, religion_shapes, religion_ltys) %>%
save_plot(., which_data="religion", plot_class="line_std")
```

```{r religion-std-barplot, include=F}
make_barplot_by_std(religion_std_summary_tab, religion_colors, 
                    "This speaker's religion is...") 
ggsave("religion_std_barplot.pdf", path="plots/by_standard/barplots", 
       height=16, width=14, units="in")
```

### With Age. 

```{r religion-age, include=F}
religion_age_df <- r %>%
  ungroup(.) %>%
  dplyr::select(
    "language", "child_age_centered", all_of(religion_vars)) %>%
  gather(., religion, selection, -language, -child_age_centered) 

religion_age_df$var_labeled <- factor(religion_age_df$religion, 
      levels=religion_vars, labels=religion_labels)

make_age_lm_plot(religion_age_df, religion_colors, religion_ltys, 
                 "This speaker's religion is...") %>%
save_plot(plot_class="age_lm", "religion")
```

### By Child Religion
```{r}
r_for_plots %>%
  filter(child_religion %in% c("hindu", "muslim")) %>%
  group_by(id, child_religion) %>%
  summarize(muslim_prop=na.mean(muslim),
            hindu_prop = na.mean(hindu)) %>%
  group_by(child_religion) %>%
  summarize(muslim_prop=na.mean(muslim_prop),
            hindu_prop = na.mean(hindu_prop))

r_for_plots %>%
  filter(child_religion=="muslim") %>%
  group_by(language) %>%
  summarize(muslim_rel_prop=na.mean(muslim),
            hindu_rel_prop = na.mean(hindu),
            jain_rel_prop = na.mean(jain),
            christ_rel_prop = na.mean(christian),
            buddhist_rel_prop=na.mean(buddhist)) 

r_for_plots %>%
  filter(child_religion=="hindu") %>%
  group_by(language) %>%
  summarize(muslim_rel_prop=na.mean(muslim),
            hindu_rel_prop = na.mean(hindu),
            jain_rel_prop = na.mean(jain),
            christ_rel_prop = na.mean(christian),
            buddhist_rel_prop=na.mean(buddhist)) 

r_for_plots %>%
  filter(child_religion %in% c("hindu", "muslim")) %>%
  summarize(muslim_rel_prop=na.mean(muslim),
            hindu_rel_prop = na.mean(hindu),
            jain_rel_prop = na.mean(jain),
            christ_rel_prop = na.mean(christian),
            buddhist_rel_prop=na.mean(buddhist)) 

r_for_plots %>%
  filter(child_religion %in% c("hindu", "muslim")) %>%
  group_by(language, child_religion) %>%
  summarize(muslim_rel_prop=na.mean(muslim),
            hindu_rel_prop = na.mean(hindu),
            jain_rel_prop = na.mean(jain),
            christ_rel_prop = na.mean(christian),
            buddhist_rel_prop=na.mean(buddhist)) 
```

## Mixed Effects Multinomial Regression  

### Language x Age  
```{r rel-mblogit, warning=F}
# dropping idks
r_for_plots <- r %>% filter(religion %in% religion_vars)
r_for_plots$religion <- factor(r_for_plots$religion, 
      levels=religion_vars, labels=religion_labels)
r_for_plots$var_labeled <- r_for_plots$religion
r_for_plots$language <- factor(r_for_plots$language, 
                               levels=language_labels)
r_for_plots$language <- relevel(r_for_plots$language, ref="Gujarati")
r_for_plots$religion <- relevel(r_for_plots$religion, ref="Hindu")
#rel_mod2 <- mblogit(religion ~ 0 + language*child_age_centered,
#                   random=~1|id,
#                   data = r_for_plots)

rel_mod <- mblogit(var_labeled ~ 0 + language*child_age_centered,
                   random=~1|id,
                   data = r_for_plots)
```

```{r rel-anova, warning=F}
rel_noint_mod <- mblogit(var_labeled ~ 0 + language + child_age_centered,
                   random=~1|id,
                   data = r_for_plots)
summary(rel_mod)

anova(rel_noint_mod, rel_mod, test="LRT") #(28) = 99.7, 0.00000000058 ***
```

#### Forest Plot  
```{r rel-mblogit-plot}
rp <- make_forest_plot(rel_mod)
r_n <- get_point_sizes(r_for_plots, "Hindu")
edited_rp <- edit_forest_plot_data(rp, r_n, ordered_facet_levels=c("Muslim",
                                        "Jain",
                                        "Christian",
                                        "Buddhist"))
updated_rp <- update_forest_plot(edited_rp, 
                                 title="This speaker's religion is...")
save_forest_plot(updated_rp, "rel_mod_with_age_interaction.pdf")
```

#### Table  
```{r relmod-table}
sjPlot::tab_model(
    rel_mod,
    show.r2 = TRUE,
    show.icc = FALSE,
    show.re.var = FALSE,
    p.style = "numeric_stars",
    emph.p = TRUE,
    file = "tables/models/primary/rel_mod_tab.html")

rel_tab_df <- readHTMLTable(here('2_speaker-associations/tables/models/primary/rel_mod_tab.html'), 
              header=T) 
rel_tab_df <- as.data.frame(rel_tab_df)
rel_tab_df_temp <- rel_tab_df
names(rel_tab_df) <- rel_tab_df[1,]
rel_tab_df <- rel_tab_df[-1,]
rel_tab_df$Predictors <- gsub("language", "", rel_tab_df$Predictors)
rel_tab_df$Predictors <- gsub("child_", "", rel_tab_df$Predictors)
rel_tab_df$Predictors <- gsub("_centered", "", rel_tab_df$Predictors)

buddhist <- rel_tab_df[,2:4]

christian <- rel_tab_df[,c(1,5:7)]
christian$space <- ""

jain <- rel_tab_df[,8:10]

muslim <- rel_tab_df[,c(1, 11:13)]
muslim$space <- ""

rel_mod_tab <- rbind(cbind(muslim, jain), cbind(christian, buddhist))

print.xtable(rel_mod_tab, type="latex", file="tables/models/primary/rel_mod_tab.tex")
```

### Child Religion

```{r rel-chirel-mod}
r_for_plots$child_MUSLIM <- plyr::mapvalues(r_for_plots$child_religion,
                                                    from=c("hindu", "muslim"),
                                                    to=c(0, 1))
r_for_plots$child_MUSLIM <- factor(r_for_plots$child_MUSLIM, levels=c(0,1))

rel_chirel_mod <- mblogit(religion ~ 0 + 
                            #language + 
                            language*child_religion + 
                            child_age_centered,
                            #language*child_age_centered,
                          r_for_plots[
                            r_for_plots$child_religion %in% religion_vars,])

summary(rel_chirel_mod)
```

```{r rel-chirel-anova}
rel_chirel_null_mod <- mblogit(religion ~ 0 + 
                            #language + 
                            language + child_religion,
                            #language*child_age_centered,
                          r_for_plots[
                            r_for_plots$child_religion %in% religion_vars, ])

anova(rel_chirel_null_mod, rel_chirel_mod, test="LRT") #X2(32)=149, p<0.001
```

#### Table  
```{r rel-chirel-mod-tab}
sjPlot::tab_model(
    rel_chirel_mod,
    show.r2 = TRUE,
    show.icc = FALSE,
    show.re.var = FALSE,
    p.style = "numeric_stars",
    emph.p = TRUE,
    file="tables/models/primary/rel_chirel_mod_tab.html")

rel_tab_df <- readHTMLTable(here(
  '2_speaker-associations/tables/models/primary/rel_chirel_mod_tab.html'), 
              header=T) 
rel_tab_df <- as.data.frame(rel_tab_df)
rel_tab_df_temp <- rel_tab_df
names(rel_tab_df) <- rel_tab_df[1,]
rel_tab_df <- rel_tab_df[-1,]
rel_tab_df$Predictors <- gsub("language", "", rel_tab_df$Predictors)
rel_tab_df$Predictors <- gsub("child_", "", rel_tab_df$Predictors)
rel_tab_df$Predictors <- gsub("_centered", "", rel_tab_df$Predictors)

buddhist <- rel_tab_df[,2:4]

christian <- rel_tab_df[,c(1,5:7)]
christian$space <- ""

jain <- rel_tab_df[,8:10]

muslim <- rel_tab_df[,c(1, 11:13)]
muslim$space <- ""

rel_mod_tab <- rbind(cbind(muslim, jain), cbind(christian, buddhist))

print.xtable(rel_mod_tab, type="latex", 
             file="tables/models/primary/rel_chirel_mod_tab.tex")
```

### Familiarity  

```{r rel-familiarity-mblogit, warning=F}
i <- read.csv(here('data/r_dfs/subsets/language_familiarity.csv'))

ri <- merge(r_for_plots, i, by=c("language", "id")) %>%
  filter(language!="Hindi",
         language!="English (India)")

rel_fam_mod <- mblogit(religion ~ 0 + language*familiar + child_age_centered,
                   random=~1|id,
                   data = ri)

summary(rel_fam_mod)
```

```{r rel-familiarity-anova, warning=F}
rel_fam_null <- mblogit(religion ~ 0 + language + familiar,
                   random=~1|id,
                   data = ri)

anova(rel_fam_mod, rel_fam_null, test="LRT")
```

#### Table  
```{r rel-familiarity-mod-tab}
sjPlot::tab_model(
    rel_fam_mod,
    show.r2 = TRUE,
    show.icc = FALSE,
    show.re.var = FALSE,
    p.style = "numeric_stars",
    emph.p = TRUE,
    file="tables/models/familiarity/rel_fam_mod_tab.html")

rel_tab_df <- readHTMLTable(
  here('2_speaker-associations/tables/models/familiarity/rel_fam_mod_tab.html'), 
              header=T) 
rel_tab_df <- as.data.frame(rel_tab_df)
rel_tab_df_temp <- rel_tab_df
names(rel_tab_df) <- rel_tab_df[1,]
rel_tab_df <- rel_tab_df[-1,]
rel_tab_df$Predictors <- gsub("language", "", rel_tab_df$Predictors)
rel_tab_df$Predictors <- gsub("child_", "", rel_tab_df$Predictors)
rel_tab_df$Predictors <- gsub("_centered", "", rel_tab_df$Predictors)

buddhist <- rel_tab_df[,2:4]

christian <- rel_tab_df[,c(1,5:7)]
christian$space <- ""

jain <- rel_tab_df[,8:10]

muslim <- rel_tab_df[,c(1, 11:13)]
muslim$space <- ""

rel_mod_tab <- rbind(cbind(muslim, jain), cbind(christian, buddhist))

print.xtable(rel_mod_tab, type="latex", 
             #include.rownames = F,
             file="tables/models/familiarity/rel_fam_mod_tab.tex")
```

### Speaker Gender  

```{r rel-gender-mod}
r_for_plots$speaker_FEMALE <- plyr::mapvalues(r_for_plots$speaker_gender,
                                                    from=c("male", "female"),
                                                    to=c(0, 1))
r_for_plots$speaker_FEMALE <- factor(r_for_plots$speaker_FEMALE, levels=c(0,1))

rel_gender_mod <- mblogit(var_labeled ~ 0 + language*speaker_FEMALE +
                            child_age_centered,
                          r_for_plots[r_for_plots$speaker_FEMALE!="",])

summary(rel_gender_mod)
# no effect of gender
```

#### Table 
```{r rel-gender-mod-tab}
sjPlot::tab_model(
    rel_gender_mod,
    show.r2 = TRUE,
    show.icc = FALSE,
    show.re.var = FALSE,
    p.style = "numeric_stars",
    emph.p = TRUE,
    file="tables/models/gender/rel_gender_mod_tab.html")

rel_tab_df <- readHTMLTable(here(
  '2_speaker-associations/tables/models/gender/rel_gender_mod_tab.html'), 
              header=T) 
rel_tab_df <- as.data.frame(rel_tab_df)
rel_tab_df_temp <- rel_tab_df
names(rel_tab_df) <- rel_tab_df[1,]
rel_tab_df <- rel_tab_df[-1,]
rel_tab_df$Predictors <- gsub("language", "", rel_tab_df$Predictors)
rel_tab_df$Predictors <- gsub("child_", "", rel_tab_df$Predictors)
rel_tab_df$Predictors <- gsub("_centered", "", rel_tab_df$Predictors)

buddhist <- rel_tab_df[,2:4]

christian <- rel_tab_df[,c(1,5:7)]
christian$space <- ""

jain <- rel_tab_df[,8:10]

muslim <- rel_tab_df[,c(1, 11:13)]
muslim$space <- ""

rel_mod_tab <- rbind(cbind(muslim, jain), cbind(christian, buddhist))

print.xtable(rel_mod_tab, type="latex", 
             file="tables/models/gender/rel_gender_mod_tab.tex")
```

+ Some effect of speaker gender on children's religion selections 

## Combining Plots  

```{r rel-combined-plots}
religion_std_summary_tab$language <- order_languages(religion_std_summary_tab$language)
rs <- ggplot(religion_std_summary_tab, 
       aes(x=standard_num, y=mean, color=var_labeled)) +
    geom_line(aes(lty=var_labeled)) + 
    geom_point(aes(shape=var_labeled)) +
    geom_errorbar(aes(ymin=cilo, ymax=cihi), width=0) +
    facet_wrap(~language, ncol=4) +
    scale_color_manual(values=religion_colors, religion_legend_title) + 
    scale_shape_manual(values=religion_shapes, religion_legend_title) +
    scale_linetype_manual(values=religion_ltys,
                          religion_legend_title) +
    ylim(0, 1) +
    scale_x_continuous(breaks=c(3, 5, 7), 
                       label=std_axis_labels) +
    sans_axes_theme_bigger +
    theme(legend.position = "bottom",
          legend.key=element_rect(color=NA),
          legend.margin = margin(-5,0,0,0)) +
    xlab("Grade") +
    ylab("Mean Proportion")

final_rp <- updated_rp + theme(axis.text.y = element_text(face="bold", size=10),
                               axis.title.y = element_text(face="bold"),
                               axis.text.x=element_text(size=10),
                               axis.title.x=element_text(face="bold", size=11),
                               legend.title = element_text(face="bold", size=11),
                               strip.text = element_text(color="gray30", 
                                                         size=11, 
                                                         face="bold.italic"),
          title=element_text(color="gray30", face="bold.italic", size=10),
          legend.key = element_rect(linewidth=0, fill=NA),
          legend.text = element_text(color="gray30", size=10),
          #legend.margin = margin(0,0,0,-5))#,
          panel.spacing.x = unit(0.4, "cm"))

rc <- grid.arrange(rs, final_rp, ncol=2, widths=c(3, 3.75))

ggsave(plot=rc, 
       "combined_rel.png", 
       path="plots/combined/", 
       device="png", width=7, height=3, scale=2, units="in")

ggsave(plot=rc, 
       "combined_rel_labeled.pdf", 
       path="plots/combined/", 
       device="pdf", width=7, height=3, scale=2, units="in")

ggsave(plot=rc, 
       "combined_rel.svg", 
       path="plots/combined/", 
       width=7, height=3, scale=2)

#ggsave(rc,  
#  labels='AUTO', widths = c(3, 3.75),
#  ncol = 2, nrow = 1, align = 'v'), 
  #width = 7, height=3, units ='in', scale=1.75)
```

## Models: Odds of Religion Selection

#### Hindu

```{r hindu-stats}
r %>% 
  mutate(total_trials=n(),
    n_trials=sum(religion=="hindu")) %>%
  distinct(id, .keep_all = T) %>%
  mutate(n_children=n(),
         prop = n_trials/total_trials) %>%
  distinct(n_trials, total_trials, prop, n_children)
```

`Hindu' selected on 31\% of trials (574/1856), by 129 children.

```{r hindu-glm, include=F}
ass_hindu_glm <- glm(
  hindu ~ child_age + language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_hindu_glm)), 2),
round(exp(confint(ass_hindu_glm)), 2))%>%
  kable(.)
```

```{r hindu-int-glm, include=F}
ass_hindu_int_glm <- glm(
  hindu ~ child_age*language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_hindu_int_glm)), 2),
round(exp(confint(ass_hindu_int_glm)), 2))%>%
  kable(.)

summary(ass_hindu_int_glm)

Anova(ass_hindu_int_glm)
```

```{r hindu-2int-glm}
ass_hindu_2int_glm <- glm(
  hindu ~ child_age*language + child_religion*language, 
  family="binomial", a[a$child_religion!="other",])

cbind(round(exp(coef(ass_hindu_2int_glm)), 2),
round(exp(confint(ass_hindu_2int_glm)), 2))%>%
  kable(.)

summary(ass_hindu_2int_glm)

Anova(ass_hindu_2int_glm)
```

#### Muslim

```{r muslim-glm,include=F}
ass_muslim_glm <- glm(
  muslim ~ child_age + language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_muslim_glm)), 2),
round(exp(confint(ass_muslim_glm)), 2))%>%
  kable(.)
```

```{r muslim-int-glm, include=F}
ass_muslim_int_glm <- glm(
  muslim ~ child_age*language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_muslim_int_glm)), 2),
round(exp(confint(ass_muslim_int_glm)), 2))%>%
  kable(.)

summary(ass_muslim_int_glm)

Anova(ass_muslim_int_glm)
```

```{r muslim-1int-glm}
ass_muslim_1int_glm <- glm(
  muslim ~ child_age + child_religion*language, 
  family="binomial", a[a$child_religion!="other",])

cbind(round(exp(coef(ass_muslim_1int_glm)), 2),
round(exp(confint(ass_muslim_1int_glm)), 2))%>%
  kable(.)

summary(ass_muslim_1int_glm)

Anova(ass_muslim_1int_glm)
```

#### Jain

```{r jain-glm, include=F}
ass_jain_glm <- glm(
  jain ~ child_age + language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_jain_glm)), 2),
round(exp(confint(ass_jain_glm)), 2))%>%
  kable(.)
```

```{r jain-int-glm, include=F}
ass_jain_int_glm <- glm(
  jain ~ child_age*language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_jain_int_glm)), 2),
round(exp(confint(ass_jain_int_glm)), 2))%>%
  kable(.)

summary(ass_jain_int_glm)

Anova(ass_jain_int_glm)
```

```{r jain-1int-glm}
ass_jain_1int_glm <- glm(
  jain ~ child_age + child_religion*language, 
  family="binomial", a[a$child_religion!="other",])

ass_jain_1int_glm_coefs <- 
  as.data.frame(cbind(round(exp(coef(ass_jain_1int_glm)), 2),
round(exp(confint(ass_jain_1int_glm)), 2)))

ass_jain_1int_glm_coefs$toss <- ass_jain_1int_glm_coefs$`2.5 %`<1 & ass_jain_1int_glm_coefs$`97.5 %`>1

ass_jain_1int_glm_coefs %>%filter(toss==0)

summary(ass_jain_1int_glm)

Anova(ass_jain_1int_glm)
```

#### Christian

```{r christian-glm, include=F}
ass_christian_glm <- glm(
  christian ~ child_age + language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_christian_glm)), 2),
round(exp(confint(ass_christian_glm)), 2))%>%
  kable(.)
```

```{r christian-int-glm, include=F}
ass_christian_int_glm <- glm(
  christian ~ child_age*language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_christian_int_glm)), 2),
round(exp(confint(ass_christian_int_glm)), 2))%>%
  kable(.)

summary(ass_christian_int_glm)

options(scipen=100)

Anova(ass_christian_int_glm)
```

```{r christian-2int-glm}
ass_christian_2int_glm <- glm(
  christian ~ child_age*language + child_religion*language, 
  family="binomial", r[r$child_religion!="other",])

ass_christian_2int_glm_coefs <- 
  as.data.frame(cbind(round(exp(coef(ass_christian_2int_glm)), 2),
                      round(exp(confint(ass_christian_2int_glm)), 2)))
ass_christian_2int_glm_coefs$toss <- ass_christian_2int_glm_coefs$`2.5 %`<1 & ass_christian_2int_glm_coefs$`97.5 %`>1

ass_christian_2int_glm_coefs %>%filter(toss==0)

summary(ass_christian_2int_glm)

options(scipen=100)

Anova(ass_christian_2int_glm)
```

#### Buddhist

```{r buddhist-glm, include=F}
ass_buddhist_glm <- glm(
  buddhist ~ child_age + language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_buddhist_glm)), 2),
round(exp(confint(ass_buddhist_glm)), 2))%>%
  kable(.)
```

```{r buddhist-int-glm, include=F}
ass_buddhist_int_glm <- glm(
  buddhist ~ child_age*language + child_religion, 
  family="binomial", r)

cbind(round(exp(coef(ass_buddhist_int_glm)), 2),
round(exp(confint(ass_buddhist_int_glm)), 2))%>%
  kable(.)

summary(ass_buddhist_int_glm)

Anova(ass_buddhist_int_glm)
```

```{r buddhist-2int-glm}
ass_buddhist_2int_glm <- glm(
  buddhist ~ child_age*language + child_religion*language, 
  family="binomial", r[r$child_religion!="other",])

ass_buddhist_2int_glm_coefs <- 
  as.data.frame(cbind(round(exp(coef(ass_buddhist_2int_glm)), 2),
round(exp(confint(ass_buddhist_2int_glm)), 2)))

ass_buddhist_2int_glm_coefs$toss <- ass_buddhist_2int_glm_coefs$`2.5 %`<1 & ass_buddhist_2int_glm_coefs$`97.5 %`>1

ass_buddhist_2int_glm_coefs %>% filter(toss==0)

summary(ass_buddhist_2int_glm)

Anova(ass_buddhist_2int_glm)
```

### No Opinion 

```{r}
ass_idk_glm <- glm(
  no_opinion_religion ~ child_age + language, 
  family="binomial", r[r$child_religion!="other",])

ass_idk_glm_coefs <- 
  as.data.frame(cbind(round(exp(coef(ass_idk_glm)), 2),
round(exp(confint(ass_idk_glm)), 2)))

ass_idk_glm_coefs$toss <- ass_idk_glm_coefs$`2.5 %`<1 & ass_idk_glm_coefs$`97.5 %`>1

ass_idk_glm_coefs %>% filter(toss==0)

summary(ass_buddhist_2int_glm)

Anova(ass_buddhist_2int_glm)
```
