---
title: "India Sociolinguistics Wealth Associations Analyses"
author: "Ruthe Foushee"
date: "2023-08-18"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r wealth-setup, include=FALSE}
library(here)
here::i_am('2_speaker-associations/2c_wealth.Rmd')

knitr::opts_chunk$set(
  echo = FALSE, message=F, warning=F,
  fig.width = 6)

source(here('isl-resources.R'))
```

```{r read-in-data}
a <- read.csv(here('data/r_dfs/subsets/associations_data.csv'))[,-1]

factor_vars <- c('study_name', 'id', 'child_sex', 'child_religion', 
                 'school', 'standard',
                 'question_type', 'language', 'speaker_gender', 
                 'origin', 'geographic_origin', 'religion', 'wealth',
                 'army_navy_language')

numeric_vars <- c('standard_num', 'child_age', 'child_age_centered', 
                  'sequence', 'coded_wealth')

a <- a %>%
  mutate_at(factor_vars, as.factor) %>%
  mutate_at(numeric_vars, as.numeric)

w <- a %>%
  filter(wealth!="")

w$language <- factor(w$language, levels=language_labels)
```

```{r wealth-no-opinion-trials}
N_TRIALS <- w %>%
  filter(no_opinion_wealth==1) %>%
  summarize(no_opinion_trials=n()) %>%
  as.numeric()

N_CHILDREN <- w %>%
  filter(no_opinion_wealth==1) %>%
  group_by(id) %>%
  summarize(no_opinion_trials=n()) %>%
  summarize(n_children=n()) %>%
  as.numeric()
  
w %>%
  filter(no_opinion_wealth==1) %>%
  group_by(id)%>%
  summarize(no_opinion_trials=n()) %>%
  group_by(no_opinion_trials) %>%
  summarize(n_children=n()) %>%
  kable(.)

w %>%
  filter(no_opinion_wealth==1) %>%
  group_by(language)%>%
  summarize(n=n()) %>%
  arrange(desc(n)) %>%
  kable(.)

#265 opted out, 61 children, most on chinese and marathi
```

"No opinion" selected on `r N_TRIALS` trials by `r N_CHILDREN` children; all children selected single response.

```{r wealth-single-trials}
table(w$wealth)
```

```{r wealth-counts-by-std}
w %>%
  group_by(standard) %>%
  mutate(n_std=n()) %>%
  group_by(standard, wealth, n_std) %>%
  reframe(n=n(),
            prop=n/n_std) %>%
  distinct(standard, wealth, n, n_std, prop)
```

```{r wealth-counts-by-lang}
w %>%
  group_by(language) %>%
  mutate(n_trials=n()) %>%
  group_by(wealth, n_trials, language) %>%
  reframe(n=n(),
            prop=n/n_trials) %>%
  distinct(wealth, language, prop)  %>%
  spread(wealth, prop)
```

```{r wealth-counts-by-lang-std}
w %>%
  group_by(standard, language) %>%
  mutate(n_trials=n()) %>%
  group_by(standard, wealth, n_trials, language) %>%
  reframe(n=n(),
            prop=n/n_trials) %>%
  distinct(standard, wealth, language, prop) %>%
  filter(wealth=="richer") %>%
  spread(standard, prop) %>%
  mutate(less_7th = `7`<`3`)

w %>%
  group_by(standard, language) %>%
  mutate(n_trials=n()) %>%
  group_by(standard, wealth, n_trials, language) %>%
  reframe(n=n(),
            prop=n/n_trials) %>%
  distinct(standard, wealth, language, prop) %>%
  spread(standard, prop) %>%
  mutate(less_7th = `7`<`3`)
#from 31--55\% of trials in 3rd to 7--34\% of trials in 7th
#(Gujarati: 39\%; Hindi: 32\%, Urdu: 31\%, Marathi: 33\%, Tamil: 37\%, Indian English: 35\%, U.S. English: 55\%, Mandarin: 51\%)

#(Gujarati: 12\%; Hindi: 12\%, Urdu: 13\%, Marathi: 12\%, Tamil: 7\%, Indian English: 34\%, U.S. English: 27\%, Mandarin: 34\%)

```
### Diverging Barchart

```{r diverging-barchart-colorway2}
wd <- w %>% filter(!is.na(coded_wealth)) %>%
              group_by(language) %>%
              mutate(mean_wealth = na.mean(coded_wealth),
                     sd_wealth = sd(coded_wealth, na.rm=T),
                     by_lang_z = (coded_wealth-mean_wealth)/sd_wealth,
                     rating_type=ifelse(
                       by_lang_z < 0, "below", "above")) %>%
              group_by(language, rating_type) %>%
              summarize(sum=sum(by_lang_z))

wd$rating_type <- factor(wd$rating_type, levels=c("below", "above"),
                         labels=c("Below\nAverage", "Above Average"))

wd$lang_rating_type <- as.character(wd$rating_type)
wd[wd$rating_type=="Above Average",]$lang_rating_type <- 
  paste("Above Average:", 
        wd[wd$rating_type=="Above Average",]$language,
        sep="\n")

lang_rating_type_colors <- c(
  "Below\nAverage" = "gray65",
  "Above Average:\nGujarati" = "#ff7f00", 
  "Above Average:\nHindi" = "#6a3d9a", # purple
  "Above Average:\nUrdu" = "#cab2d6", # magenta
  "Above Average:\nMarathi" = "#fdbf6f", # goldenrod 
  "Above Average:\nTamil" = "#e31a1c", # burnt orange
  "Above Average:\nEnglish (India)" = "#33a02c",
  "Above Average:\nEnglish (U.S.)" = "#b2df8a",
  "Above Average:\nMandarin" = "#f781bf"
)

ggplot(wd, 
       aes(x=fct_rev(language), y=sum)) + 
  geom_bar(stat="identity", aes(fill=lang_rating_type), width=.5)  +
  scale_fill_manual(name="Relative Wealth", 
                    values=lang_rating_type_colors) + 
    #scale_fill_manual(name="Predicted Wealth", 
    #                values=lang_rating_type_colors) + 
  #labels = c("Above Average", "Below Average"), 
  #values = c("gray65", "#31a354")) + 
  #facet_wrap(~language, ncol=3) +
  xlab("Language") +
  #ylim(-100, 100) +
  ylab("Normalized Predicted Wealth") +
  sans_axes_theme +
  theme(axis.text.y=element_text(size=10, color="gray30", 
                                 family="sans"),
        legend.text = element_text(size=8),
        legend.title = element_text(size=10),
        legend.key = element_rect(color=NA),
        legend.position = "bottom",
        legend.title.position = "top",
        legend.margin = margin(0,0,0,-55)) +
  coord_flip() 

ggsave("wealth_diverging_barplot_colored.pdf", device = "pdf", 
       path = "plots/barplots_overall/",
       scale = 1, width = 6, height = 6, units = "in")
```

## Categorically: "Less $"/"As Much $"/"More $"

```{r wealth-overall-barplot, include=F}
wealth_summary_tab <- w %>%
  ungroup(.) %>%
  dplyr::select("language", all_of(wealth_vars)) %>%
  gather(., wealth, selection, -language) %>%
    group_by(language, wealth) %>%
    summarize(mean=na.mean(selection),
              cilo = mean-ci.low(selection),
              cihi = mean+ci.high(selection)) 

wealth_summary_tab$wealth <- factor(
  wealth_summary_tab$wealth, 
  levels=wealth_vars, 
  labels=wealth_labels)

ggplot(wealth_summary_tab, 
       aes(x=wealth, y=mean, fill=wealth)) +
    geom_bar(stat="identity") + 
    geom_errorbar(aes(ymin=cilo, ymax=cihi), width=0, 
                  color=line_color) + 
    facet_wrap(~language, ncol=2) +
    scale_fill_manual(values = wealth_colors,
                      wealth_legend_title1) +
    ylim(0, 1) +
    sans_theme +
    theme(legend.title = element_text(
      size=10, colour="gray30", family="sans", face="italic")) +
    ylab("Mean")

ggsave("wealth_associations.png", device = "png", 
       path = "plots/",
       scale = 1, width = 7, height = 6, units = "in")
```

### Over Time

#### By Standard
##### Plots
```{r wealth-std-lineplot}
wealth_std_summary_tab <- w %>%
  ungroup(.) %>%
  dplyr::select("language", "standard", "standard_num",
    all_of(wealth_vars)) %>%
  gather(., wealth, selection, -language, -standard, -standard_num) %>%
    group_by(language, standard, standard_num, wealth) %>%
    summarize(mean=na.mean(selection),
              cilo = mean-ci.low(selection),
              cihi = mean+ci.high(selection)) 

wealth_std_summary_tab$wealth <- factor(
  wealth_std_summary_tab$wealth, 
  levels=wealth_vars, 
  labels=wealth_labels)

ggplot(wealth_std_summary_tab, 
       aes(x=standard_num, y=mean, color=wealth)) +
    geom_line(aes(lty=wealth)) + 
    geom_point(aes(shape=wealth)) +
    geom_errorbar(aes(ymin=cilo, ymax=cihi), width=0) +
    facet_wrap(~language, ncol=4) +
    scale_color_manual(values=wealth_colors, wealth_legend_title) + 
    scale_shape_manual(values=wealth_shapes, wealth_legend_title) +
    scale_linetype_manual(values=wealth_ltys,
                          wealth_legend_title) +
    ylim(0, 1) +
    scale_x_continuous(breaks=c(1, 2, 3), 
                       label=std_axis_labels) +
   # labs(title="wealth Associations Across Standards 3-7") +
    sans_axes_theme +
    theme(legend.position = "bottom") +
    xlab("Grade") +
    ylab("Mean Proportion")
  
ggsave("wealth_std.pdf", device = "pdf", 
       path = "plots/by_standard/line_plots",
       scale = 1, width = 7, height = 5, units = "in")
```

```{r wealth-std-barplot, include=F}
ggplot(wealth_std_summary_tab, 
       aes(x=wealth, y=mean, fill=wealth)) +
    geom_bar(stat="identity") + 
    geom_errorbar(aes(ymin=cilo, ymax=cihi), width=0, 
                  color=line_color) + 
    facet_wrap(~language + standard, ncol=3) +
    scale_fill_manual(values = wealth_colors, wealth_legend_title1) +
    ylim(0, 1) +
    xlab("Standard") +
    ylab("Mean Proportion") +
    sans_axes_theme +
    theme(legend.title = element_text(
      size=10, colour="gray30", family="sans", face="italic"))

ggsave("wealth_std.pdf", device = "pdf", 
       path = "plots/by_standard/barplots",
       scale = 1, width = 7, height = 5, units = "in")
```

#### With Age
##### Plots 
```{r wealth-age, include=F}
wealth_age_df <- w %>%
  ungroup(.) %>%
  dplyr::select(
    "language", "child_age", all_of(wealth_vars)) %>%
  gather(., wealth, selection, -language, -child_age) 

wealth_age_df$wealth <- factor(wealth_age_df$wealth, 
      levels=wealth_vars, labels=wealth_labels)

ggplot(wealth_age_df, 
       aes(x=child_age, y=selection, color=wealth, lty=wealth, fill=wealth)) +
    stat_smooth(aes(x=child_age, y=selection), 
                method="lm", level=.75, fullrange=T) +
    facet_wrap(~language, ncol=4) +
    scale_color_manual(values = wealth_colors, wealth_legend_title1) +
    scale_linetype_manual(values=wealth_ltys, wealth_legend_title1) +
    scale_fill_manual(values=wealth_colors, wealth_legend_title1) +
    ylim(0, 1) +
    ylab("Mean") +
    xlab("Child Age (yrs)") +
    #labs(title="wealth Associations with Age") +
    sans_axes_theme +
    theme(legend.title = element_text(
      size=10, colour="gray30", family="sans", face="italic"))

ggsave("wealth_age_lm.png", device = "png", 
       path = "plots/by_age/",
       scale = 1, width = 7, height = 6, units = "in")
```

## Ordinal Logistic Regression

```{r}
w %>%
  group_by(wealth) %>%
  summarize(n=n())

w_for_plots <- w %>%
  filter(wealth!="idk")

w_for_plots$wealth <- factor(w_for_plots$wealth, 
                             levels=c("poorer", "same", "richer"))
w_for_plots$language <- relevel_languages(w_for_plots$language)

w_ord_ageint_mod <- clmm(wealth ~ language*child_age_centered + 
                    (1|id), link="logit", w_for_plots)

w_ord_mod <- clmm(wealth ~ 0 + language + child_age_centered + 
                    (1|id), link="logit", w_for_plots)

w_ord_noage_mod <- clmm(wealth ~ language + 
                    (1|id), link="logit", w_for_plots)
```

```{r}
summary(w_ord_mod)
anova(w_ord_ageint_mod, w_ord_mod)

anova(w_ord_mod, w_ord_noage_mod)
#($\chi^{2}(7)=8.03$, $p=0.33$)
```

#### Table 

```{r}
sjPlot::tab_model(
    w_ord_mod,
    show.r2 = TRUE,
    show.icc = FALSE,
    show.re.var = FALSE,
    p.style = "numeric_stars",
    emph.p = TRUE, 
    file = "tables/models/primary/w_ord_mod_tab.html")

w_tab_df <- readHTMLTable(here(
  '2_speaker-associations/tables/models/primary/w_ord_mod_tab.html'),
  header=T) 

w_tab_df <- as.data.frame(w_tab_df)
names(w_tab_df) <- w_tab_df[1,]
w_tab_df <- w_tab_df[-1,]

print.xtable(w_tab_df, type="latex", file="tables/models/primary/w_ordinal_tab.tex")
```

#### Forest Plot

```{r w-ordmod-plot}
wp <- make_forest_plot(w_ord_mod)
  wp$data$term <- gsub("language", "", wp$data$term)
  wp$data$term <- factor(wp$data$term, 
                              levels=language_labels) %>%
    fct_rev(.)
 # wp$data$facet <- "less money  . . .  as much money  . . .  more money"
  wp$data$facet <- "less $$ . . . as much $$ . . . more $$"
  wp$data <- wp$data[!is.na(wp$data$term), ]
  
final_wp <- wp + geom_hline(yintercept=1, lty=2, color="gray50") + 
  facet_grid(~facet) + 
    theme(panel.background = element_rect(fill=NA, color="gray30"),
          panel.grid = element_line(color="gray60", linetype="dotted"),
          strip.background = element_rect(fill="gray90", color="gray30"),
          strip.text = element_text(color="gray30", size=12, face="bold.italic"),
          title=element_text(color="gray30", face="bold.italic"),
          legend.key = element_rect(linewidth=0, color=NA),
          legend.text = element_text(color="gray30", size=10),
          axis.text = element_text(color="gray30", size=10, face="plain"),
          axis.title.x=element_text(color="gray30", size=11,
                                    face="plain")) +
    scale_color_manual(values=c("#fc8d59", "#99d594")) + ##33a02c
    labs(title="This speaker has...")
  #labs(title="")

ggsave("wp_mod_no_interaction.png", final_wp, device="png", 
       path="plots/forest_plots/", scale = 1, width = 4, height = 6, units = "in")
```

### Familiarity
```{r}
i <- read.csv(here('data/r_dfs/subsets/language_familiarity.csv'))
wi <- merge(w_for_plots, i, by=c("language", "id")) %>%
  filter(language!="English (India)",
         language!="Hindi")

wi <- merge(w_for_plots, i, by=c("language", "id"))
wi$familiar <- factor(wi$familiar, levels=c(0, 1))

w_fam_mod <- clmm(wealth ~ language*familiar + child_age_centered + 
                    (1|id), link="logit", wi)
```

#### Table 

```{r}
sjPlot::tab_model(
    w_fam_mod,
    show.r2 = TRUE,
    show.icc = FALSE,
    show.re.var = FALSE,
    p.style = "numeric_stars",
    emph.p = TRUE, 
    show.reflvl = TRUE,
    file = "tables/models/familiarity/w_fam_mod_tab.html")

w_tab_df <- readHTMLTable(here(
  '2_speaker-associations/tables/models/familiarity/w_fam_mod_tab.html'),
  header=T) 

w_tab_df <- as.data.frame(w_tab_df)
names(w_tab_df) <- w_tab_df[1,]
w_tab_df <- w_tab_df[-1,]

print.xtable(w_tab_df, type="latex", file="tables/models/familiarity/w_fam_mod_tab.tex")
```

### Gender
```{r}
w_for_plots$speaker_FEMALE <- plyr::mapvalues(w_for_plots$speaker_gender,
                                                    from=c("male", "female"),
                                                    to=c(0, 1))
w_for_plots$speaker_FEMALE <- factor(w_for_plots$speaker_FEMALE, levels=c(0,1))
w_for_plots$language <- relevel(w_for_plots$language, ref="Gujarati")
w_gender_mod <- clmm(wealth ~ language*speaker_FEMALE + child_age_centered + 
                    (1|id), link="logit",
                    w_for_plots[w_for_plots$speaker_gender!="",])
```


#### Table 

```{r}
sjPlot::tab_model(
    w_gender_mod,
    show.r2 = TRUE,
    show.icc = FALSE,
    show.re.var = FALSE,
    p.style = "numeric_stars",
    emph.p = TRUE, 
    file = "tables/models/gender/w_gender_mod_tab2.html")

w_tab_df <- readHTMLTable(here(
  '2_speaker-associations/tables/models/gender/w_gender_mod_tab2.html'),
  header=T) 

w_tab_df <- as.data.frame(w_tab_df)
names(w_tab_df) <- w_tab_df[1,]
w_tab_df <- w_tab_df[-1,]

print.xtable(w_tab_df, type="latex", file="tables/models/gender/w_gender_mod_tab2.tex")
```

## Analyzed as a Continuous Variable 

Recoded responses to prompt "This speaker has...": 

* -1: "*Less* money than the people in my city" 

* 0: "*As much* money as the people in my city" 

* 1: "*More* money than the people in my city"

* NA: "No Opinion"

```{r recoded-wealth-df}
coded_wealth_df <- w %>% filter(!is.na(coded_wealth)) %>%
  group_by(language) %>%
  mutate(mean_wealth = na.mean(coded_wealth))

coded_wealth_df <- coded_wealth_df %>%
  filter(!is.na(language))
```

```{r recoded-wealth-barplots-colored}
wb <- coded_wealth_df %>%
  group_by(language)%>%
  summarize(mean = mean(coded_wealth),
            cilo = mean - ci.low(coded_wealth),
            cihi = mean + ci.high(coded_wealth)) %>%
ggplot(., 
       aes(x=language, y=mean)) +
    geom_bar(stat="identity", aes(fill=language), alpha=0.9) +
    geom_hline(yintercept=0, lty=2, colour=line_color) +
    scale_fill_manual(values=language_colors, name="Language") +
    geom_errorbar(aes(ymin=cilo, ymax=cihi), width=0, color=line_color) +
    scale_color_manual(values=language_colors, name="Language (audio)") +
    ylim(-0.4, 0.6) +
    #labs(title='Relative Wealth Associations by Language\n(0="As much money as the people in my city"') +
    ylab("Comparative Wealth") + 
    xlab("Language (audio)") +
    sans_axes_theme_bigger +
  theme(axis.text.x=element_text(angle=60, hjust=1, face="bold"),
        legend.position = "none")

ggsave("wealth_recoded_meaned_barplot.pdf", device = "pdf", 
       path = "plots/barplots_overall/",
       scale = 1, width = 7, height = 6, units = "in")
```

### With Age  

```{r recoded-wealth-age}
coded_wealth_df$language <- relevel_languages(coded_wealth_df$language)

wal <- ggplot(coded_wealth_df, 
       aes(x=child_age, y=coded_wealth)) +
    geom_segment(aes(y=0, yend=0, x=7.2, xend=13), lty=2, 
                 colour="gray20", linewidth = .75) +
    stat_smooth(aes(x=child_age, y=coded_wealth, 
                    color=language, fill=language),
                method="lm", level=.75, fullrange=T) +
    scale_color_manual(values=language_colors, name="Language") +
    scale_fill_manual(values=language_colors, name="Language") +
    facet_wrap(~language, ncol=4) +
    ylim(-0.5, 1) +
    ylab("Comparative Wealth") + 
    xlab("Child Age (years)") +
    sans_axes_theme_bigger +
  theme(legend.position = "none")

ggsave("wealth_recoded_age_lm.png", device = "png", 
       path = "plots/by_age/",
       scale = 1.5, width = 6, height = 4, units = "in")

ggsave("wealth_recoded_age_lm_short.pdf", device = "pdf", 
       path = "plots/by_age/",
       scale = 2, width = 4, height = 2.5, units = "in")

ggsave("wealth_recoded_age_lm_6in.pdf", device = "pdf", 
       path = "plots/by_age",
       scale = 1.5, width = 6, height = 4, units = "in")
```

```{r recoded-combined-plots}
wc <- ggarrange(wal, wb + ylim(-0.5, 1), 
          labels='AUTO', widths = c(4, 3), 
          ncol = 2, nrow = 1, align = 'v')

save_combined_plot_svg(wc, "combined_wealth_labeled.svg")
```

## LMERs

```{r recoded-wealth-lmer}
wealth_lmer <- lmer(coded_wealth ~ language + 
                      child_age_centered + (1|id), w)

cbind(fixef(wealth_lmer), confint(wealth_lmer)[3:11,]) %>%
  kable(., caption="Wealth Model Fixed Effects")
```

```{r recoded-wealth-int-lmer}
wealth_int_lmer <- lmer(
  coded_wealth ~ language*child_age_centered + (1|id),
                    w)

cbind(fixef(wealth_int_lmer), confint(wealth_int_lmer)[3:18,]) %>%
  kable(., caption="Wealth Interaction Model Fixed Effects")

anova(wealth_lmer, wealth_int_lmer)

Anova(wealth_int_lmer)

wealth_int_lm <- lm(
  coded_wealth ~ language*child_age_centered,
                    w)
```

The interaction between language and child age is not significant in predicting children's speaker--wealth associations.

```{r}
w$speaker_FEMALE <- plyr::mapvalues(w$speaker_gender,
                                                    from=c("male", "female"),
                                                    to=c(0, 1))
w$speaker_FEMALE <- as.numeric(
  as.character(
    w$speaker_FEMALE))

w$language <- relevel(w$language, ref="Gujarati")
w_gender_mod <- lmer(coded_wealth ~ 0 + language*speaker_FEMALE + 
                       child_age_centered + (1|id), w)

stargazer(w_gender_mod, ci=T, ci.separator = "--", digits=2,
          star.cutoffs=c(0.05, 0.01, 0.001), single.row = T) 
```

### Language ID  

```{r recoded-wealth-id-int-lmer}
wealth_id_lmer <- lmer(
  coded_wealth ~ language*familiar + child_age_centered + (1|id),
                    wi)

cbind(fixef(wealth_id_lmer), confint(wealth_id_lmer)[3:18,]) %>%
  kable(., caption="Wealth-ID Interaction + Age Model Fixed Effects")

#anova(wealth_id_lmer, wealth_int_lmer)

Anova(wealth_id_lmer)
```

```{r recoded-wealth-ida-int-lmer}
wealth_idint_lmer <- lmer(
  coded_wealth ~ language*familiar*child_age_centered + (1|id),
                    wi)

cbind(fixef(wealth_idint_lmer), confint(wealth_idint_lmer)[3:32,]) %>%
  kable(., caption="Wealth Interaction Model Fixed Effects")

#anova(wealth_id_lmer, wealth_idint_lmer)

Anova(wealth_idint_lmer)
```
