---
title: "India Sociolinguistics Learning Prediction Analyses"
author: "Ruthe Foushee"
date: "2023-08-17"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r faces-setup, include=FALSE}
library(here)
here::i_am('4_learning/4_learning-predictions.Rmd')

knitr::opts_chunk$set(
  echo = FALSE, message=F, warning=F,
  fig.width = 6)

source(here('isl-resources.R'))
```

```{r l-read-in-data}
l <- read.csv(here('data/r_dfs/subsets/learning_predictions_data.csv'))[,-1]

factor_vars <- c('study_name', 'id', 'child_sex', 'child_religion', 
                 'school', 'standard',
                 'question_type', 'presentation',
                 'language', 'speaker_gender', 
                 'face', 'army_navy_language', 'rating_cat',
                 'rating_cat_w_idk')

numeric_vars <- c('standard_num', 'child_age', 'child_age_centered', 
                  'sequence', 'rating_num')

l <- l %>%
  mutate_at(factor_vars, as.factor) %>%
  mutate_at(numeric_vars, as.numeric)

l$language <- factor(
  l$language, 
  levels=language_name_vars[c(1:2,5:7)], 
  labels=language_name_labels[c(1:2,5:7)])

l$face <- factor(
  l$face, 
  levels=face_vars[1:5],
  labels=face_labels[1:5])
```

```{r l-vars}
l$rating_cat <- factor(l$rating_cat, 
                       levels=c("Not at all", "Medium", "Very well"))
l$rating_cat <- relevel(l$rating_cat, ref="Medium")

n_trials <- nrow(l[!is.na(l$rating_cat_w_idk),])

l %>%
  filter(!is.na(rating_cat_w_idk)) %>%
  ungroup() %>%
  group_by(rating_cat_w_idk) %>%
  summarize(n=n(),
            prop=n/n_trials)
```

```{r l-idk}
l %>%
  filter(rating_cat_w_idk=="No opinion") %>%
  ungroup() %>%
  mutate(n_total_trials=n()) %>%
  distinct(id, .keep_all = T) %>%
  group_by(n_total_trials) %>%
  reframe(n_total_children=n()) 

l %>%
  filter(rating_cat_w_idk=="No opinion") %>%
  ungroup() %>%
  group_by(face) %>%
  mutate(n_trials=n()) %>%
  distinct(id, .keep_all = T) %>%
  group_by(face, n_trials) %>%
  reframe(n_children=n())
```
No children selected multiple options. The most frequent selection was "Medium" (1033 trials, 38\% of trials), followed by ``Very well'' (849, 31\%), "Not at all'' (705, 26\%), and "No opinion" (127 trials from 37 children; 32 dravidian, 28 asian, 25 hindu, 23 muslim, 19 white).

```{r l-summs}
l %>%
  group_by(rating_cat, face) %>%
  summarize(n=n())


l %>%
  group_by(face, rating_cat) %>%
  summarize(n=n())

l %>%
  group_by(language, face) %>%
  summarize(none=na.sum(rating_cat=="Not at all"),
            medium=na.sum(rating_cat=="Medium"),
            well=na.sum(rating_cat=="Very well"))

l %>%
  filter(!is.na(rating_cat_w_idk)) %>%
  group_by(language, face) %>%
  summarize(n=n())

l %>%
  filter(!is.na(rating_cat_w_idk)) %>%
  group_by(language, face) %>%
  summarize(n_3rd=sum(standard=="3"),
            n_5th=sum(standard=="5"),
            n_7th=sum(standard=="7"))


table(l[!is.na(l$rating_cat_w_idk),]$language, l[!is.na(l$rating_cat_w_idk),]$face)
```

```{r}
l %>%
  filter(language=='"Gujarati"') %>%
  mutate(n=n()) %>%
  group_by(language, face, n) %>%
  summarize(none=na.sum(rating_cat=="Not at all"),
            medium=na.sum(rating_cat=="Medium"),
            well=na.sum(rating_cat=="Very well"))
```
Gujarati: Most frequently selection "None" for Asian face, "Medium" for Dravidian, Muslim, and White, and "Very well" for Hindu face. 

```{r}
l %>%
  filter(language=='"Hindi"') %>%
  group_by(language, face) %>%
  summarize(none=na.sum(rating_cat=="Not at all"),
            medium=na.sum(rating_cat=="Medium"),
            well=na.sum(rating_cat=="Very well"))
```
Hindi: Most frequently selection "None" for Asian face, "Medium" for Dravidian and White, and "Very well" for Hindu and Muslim faces. 

```{r}
l %>%
  filter(language=='"Tamil"') %>%
  group_by(language, face) %>%
  summarize(none=na.sum(rating_cat=="Not at all"),
            medium=na.sum(rating_cat=="Medium"),
            well=na.sum(rating_cat=="Very well"))

l %>% filter(language=='"Tamil"') %>%
  group_by(language, face, standard) %>%
  summarize(none=na.sum(rating_cat=="Not at all"),
            medium=na.sum(rating_cat=="Medium"),
            well=na.sum(rating_cat=="Very well"))
```
Tamil: Most frequently selection "None" for Asian and White faces, "Medium" for Hindu and Muslim, and "Very well" for Dravidian faces. 

```{r}
l %>%
  filter(language=='"Chinese"') %>%
  group_by(language, face) %>%
  summarize(none=na.sum(rating_cat=="Not at all"),
            medium=na.sum(rating_cat=="Medium"),
            well=na.sum(rating_cat=="Very well"))
```
Mandarin: Most frequently selection "None" for Muslim and Dravidian faces, tied with "Medium" for Hindu, "Medium" for White, and "Very well" for Asian faces. 

```{r}
l %>%
  filter(language=='"English"') %>%
  group_by(language, face) %>%
  summarize(none=na.sum(rating_cat=="Not at all"),
            medium=na.sum(rating_cat=="Medium"),
            well=na.sum(rating_cat=="Very well"))
```

# Response Analyzed Categorically  

```{r}
#random=~1|id, 
#l$language <- factor(l$language, )
#l$language <- relevel(l$language, ref="Gujarati")
learn_mod <- mblogit(rating_cat ~ 0 + language*face*child_age_centered, l)
learn_mod <- mblogit(rating_cat ~ 0 + language + face + child_age_centered +
                       language:face + language:child_age_centered + 
                       face:child_age_centered + language:face:child_age_centered, l)

#learn_mod <- mblogit(rating_cat ~0 + language*face*child_age_centered,
#                     random=~1|id, l)

learn_mod <- mblogit(rating_cat ~0 + language*face*child_age_centered,
                     random=~1|id, l)
learn_null_mod <- mblogit(rating_cat ~ 0 + language*face + 
                            language:child_age_centered + 
                            face:child_age_centered, l)

anova(learn_mod, learn_null_mod, test="Chisq")

sjPlot::tab_model(
      learn_mod, 
      show.r2 = TRUE, 
      show.icc = FALSE, 
      show.re.var = FALSE, 
      p.style = "numeric_stars", 
      emph.p = TRUE, 
      file = "tables/learn_mod_explicit_tab.html")

sjPlot::tab_model(learn_mod)
plot_model(learn_mod, type = "pred", terms = c("language", "face"))
```

```{r}
l$rating_cat <- factor(l$rating_cat, levels=c("Not at all", "Medium", "Very well"))
l$rating_cat <- relevel(l$rating_cat, ref="Not at all")
```


```{r}
learn_mod <- mblogit(rating_cat ~ 0 + face*child_age_centered, l)
learn_mod <- mblogit(rating_cat ~ 0 + face + child_age_centered +
                       face:child_age_centered, l)

#learn_mod <- mblogit(rating_cat ~0 + language*face*child_age_centered,
#                     random=~1|id, l)

learn_mod <- mblogit(rating_cat ~0 + language*face*child_age_centered,
                     random=~1|id, l)
learn_null_mod <- mblogit(rating_cat ~ 0 + language*face + 
                            language:child_age_centered + 
                            face:child_age_centered, l)

anova(learn_mod, learn_null_mod, test="Chisq")

sjPlot::tab_model(
      learn_mod, 
      show.r2 = TRUE, 
      show.icc = FALSE, 
      show.re.var = FALSE, 
      p.style = "numeric_stars", 
      emph.p = TRUE, 
      file = "tables/learn_mod_explicit_tab.html")

sjPlot::tab_model(learn_mod)
plot_model(learn_mod, type = "pred", terms = c("language", "face"))
```


```{r}
summary(m1.or)

ratex  <- base::readRDS(url("https://slcladal.github.io/data/ratex.rda", "rb"))

m1.or <- clmm(Accent ~ (1|Rater) + Family*Group, link="logit", data = ratex[complete.cases(ratex),])

exp(0.43)/exp(1.60)
exp(1.42)/exp(1.60)

```


```{r learning-lang-face, include=F}
learning_summary_tab <- l %>%
  group_by(language, face) %>%
  summarize(mean=na.mean(rating),
            cilo = mean-ci.low(rating),
            cihi = mean+ci.high(rating)) 
            
ggplot(learning_summary_tab, 
       aes(x=face, y=mean, fill=face)) +
  geom_bar(stat="identity", aes(x=face, y=mean, fill=face)) + 
  geom_errorbar(aes(ymin=cilo, ymax=cihi), width=0, 
                color=line_color) + 
  facet_wrap(~language, ncol=2) +
  scale_fill_manual(values = face_colors[1:5], 
                    name=face_legend_title, 
                    labels=face_labels[1:5]) +
  labs(title='How well will she come to learn...?') +   
  scale_y_continuous(breaks=c(0, 1, 2),
                     label=c("0%", "50%", "100%")) +
  sans_theme +
  ylab("Mean Predicted Learning") +
  theme(axis.text.y = element_text(
    size=10, colour="gray30", family="sans"),
    plot.title = element_text(face="italic", size=10)) 

ggsave("learning_faces_barplot.png", device = "png", 
       path = "plots/",
       scale = 1, width = 6, height = 6, units = "in")
```

```{r learning-lang-face-std}
face_legend_title1 <- "Face:"
learning_std_summary_tab <- l %>%
  group_by(language, standard, standard_num, face) %>%
  summarize(mean=na.mean(rating),
            cilo = mean-ci.low(rating),
            cihi = mean+ci.high(rating))

lp <- ggplot(learning_std_summary_tab, 
       aes(x=standard_num, y=mean, color=face)) +
  geom_line(aes(lty=face)) +
  geom_point(aes(shape=face)) + 
  geom_errorbar(aes(ymin=cilo, ymax=cihi), width=0) + 
  facet_wrap(~language, ncol=3) +
  scale_color_manual(values = face_colors[1:5], name=face_legend_title1, labels=face_labels[1:5]) + 
  scale_shape_manual(values = face_shapes[1:5], name=face_legend_title1, labels=face_labels[1:5]) +
  scale_linetype_manual(values = face_ltys[1:5], name=face_legend_title1, labels=face_labels[1:5]) +
  # ylim(0, 2) +
  scale_x_continuous(breaks=c(3, 5, 7), 
                     label=std_axis_labels) +   
  scale_y_continuous(breaks=c(0, 1, 2),
                     label=c("0%", "50%", "100%")) +
                     #label=c("0%\nNot at all", "50%\nMedium", "100%\nVery well")) +
  sans_axes_theme +
  #theme(legend.position = "bottom",
  #      axis.text.y=element_text(face="italic")) +
  xlab("Grade") +
  labs(title='How well will she come to learn...?') +
  sans_axes_theme +
  ylab("Mean Predicted Learning") +
  theme(axis.text.y = element_text(
    size=10, colour="gray30", family="sans"),
    plot.title = element_text(face="bold.italic", size=10),
    legend.position="bottom") 

lp_final <- lp + theme(plot.title=element_text(size=0),
           legend.key = element_rect(color=NA))

ggsave("learning_faces_std.png", device = "png", 
       path = "plots/final/",
       scale = 1, width = 7, height = 5, units = "in")
```


### HINDU Face

```{r hindu-rating}
hindu_lmer <- lmer(rating ~ 0 + language + child_age_centered + (1|id), 
                   l[l$face=='HINDU', ])

#hindu_lm <- lm(rating ~ language + child_age, l[l$face=='hindu_face'])
summary(hindu_lmer)
Anova(hindu_lmer)

learning_face_hindu_lmer_coefs <- as.data.frame(
  cbind(fixef(hindu_lmer), confint(hindu_lmer)[3:8]))

learning_face_hindu_lmer_coefs %>% round(., 2)
#learning_face_hindu_lm_coefs$toss <- learning_face_hindu_lm_coefs$`2.5 %`<1 #& learning_face_hindu_lm_coefs$`97.5 %`>1

#learning_face_hindu_lm_coefs %>%filter(toss==0)
```
            
            Language: ($`r reportFTest(hindu_lmer, "language")`$),
            *English: ($`r reportCoefs(learning_face_hindu_lmer_coefs,
            'language"English"')`$)
            *Gujarati: ($`r reportCoefs(learning_face_hindu_lmer_coefs, 'language"Gujarati"')`$)
            *Hindi: ($`r reportCoefs(learning_face_hindu_lmer_coefs, 'language"Hindi"')`$)
            *Tamil: ($`r reportCoefs(learning_face_hindu_lmer_coefs, 'language"English"')`$)
            
            
```{r hindu-rating-int, include=F}
#hindu_int_lmer <- lmer(rating ~ language*child_age + (1|id), l[l$face=='HINDU',])
#summary(hindu_lmer)
#Anova(hindu_lmer)
#anova(hindu_lmer, hindu_int_lmer)
```
            
### MUSLIM Face
            
```{r muslim-rating}
muslim_lmer <- lmer(rating ~ 0 + language + child_age + (1|id), l[l$face=='MUSLIM',])
summary(muslim_lmer)
Anova(muslim_lmer)

learning_face_muslim_lmer_coefs <- cbind(fixef(muslim_lmer), confint(muslim_lmer)[3:8,]) %>% round(., 2)
```
            
            Language: ($`r reportFTest(muslim_lm, "language")`$),
            Child age: ($`r reportFTest(muslim_lm, "child_age")`$),
            *English: ($`r reportCoefs(learning_face_muslim_lm_coefs, "languageenglish")`$)
            *Gujarati: ($`r reportCoefs(learning_face_muslim_lm_coefs, "languagegujarati")`$)
            *Hindi: ($`r reportCoefs(learning_face_muslim_lm_coefs, "languagehindi")`$)
            Tamil: ($`r reportCoefs(learning_face_muslim_lm_coefs, "languagetamil")`$)
            *Child age: ($`r reportCoefs(learning_face_muslim_lm_coefs, "child_age")`$)
            
```{r muslim-rating-int, include=F}
#muslim_int_lmer <- lmer(rating ~ language*child_age_centered + (1|id), 
                    #l[l$face=='MUSLIM',])
#summary(muslim_lmer)
#Anova(muslim_lmer)
#anova(muslim_int_lmer, muslim_lmer)
```
            
### DRAVIDIAN Face
            
```{r dravidian-rating}
            dravidian_lm <- lm(rating ~ language + child_age, l[l$face=='dravidian_face' & l$language!="marathi",])
            summary(dravidian_lm)
            Anova(dravidian_lm)
            
            learning_face_dravidian_lm_coefs <- cbind(coef(dravidian_lm), confint(dravidian_lm)) %>% round(., 2)
            
```
            
            Language: ($`r reportFTest(dravidian_lm, "language")`$),
            *English: ($`r reportCoefs(learning_face_dravidian_lm_coefs, "languageenglish")`$)
            *Gujarati: ($`r reportCoefs(learning_face_dravidian_lm_coefs, "languagegujarati")`$)
            *Hindi: ($`r reportCoefs(learning_face_dravidian_lm_coefs, "languagehindi")`$)
            *Tamil: ($`r reportCoefs(learning_face_dravidian_lm_coefs, "languagetamil")`$)
            
```{r dravidian-rating-int, include=F}
            dravidian_lm <- lm(rating ~ language*child_age, l[l$face=='dravidian_face',])
            summary(dravidian_lm)
            Anova(dravidian_lm)
```
            
### ASIAN Face
            
```{r asian-rating, include=F}
            asian_lm <- lm(rating ~ language + child_age, l[l$face=='asian_face',])
            summary(asian_lm)
            Anova(asian_lm)
```
            
```{r asian-rating-int}
            asian_lm <- lm(rating ~ language*child_age, l[l$face=='asian_face' & l$language!="marathi",])
            summary(asian_lm)
            Anova(asian_lm)
            
            learning_face_asian_lm_coefs <- cbind(coef(asian_lm), confint(asian_lm)) %>% round(., 2)
```
            
            Language: ($`r reportFTest(asian_lm, "language")`$),
            Child age: ($`r reportFTest(asian_lm, "child_age")`$),
            Interaction: ($`r reportFTest(asian_lm, "language:child_age")`$),
            *English: ($`r reportCoefs(learning_face_asian_lm_coefs, "languageenglish")`$)
            *Gujarati: ($`r reportCoefs(learning_face_asian_lm_coefs, "languagegujarati")`$)
            *Hindi: ($`r reportCoefs(learning_face_asian_lm_coefs, "languagehindi")`$)
            *Tamil: ($`r reportCoefs(learning_face_asian_lm_coefs, "languagetamil")`$)
            *languagetamil:child_age: ($`r reportCoefs(learning_face_asian_lm_coefs, "languagetamil:child_age")`$)
            
### WHITE Face
            
```{r white-rating}
            white_lm <- lm(rating ~ language*child_age, l[l$face=='white_face' & l$language!="marathi",])
            summary(white_lm)
            Anova(white_lm)
            mean(as.numeric(l[l$face=='asian_face' & l$language!="marathi",]$rating))
            learning_face_white_lm_coefs<- cbind(coef(white_lm), confint(white_lm)) %>% round(., 2)
```
            
            Language: ($`r reportFTest(white_lm, "language")`$),
            Child age: ($`r reportFTest(white_lm, "child_age")`$),
            Interaction: ($`r reportFTest(white_lm, "language:child_age")`$),
            *English: ($`r reportCoefs(learning_face_white_lm_coefs, "languageenglish")`$)
            *Gujarati: ($`r reportCoefs(learning_face_white_lm_coefs, "languagegujarati")`$)
            Hindi: ($`r reportCoefs(learning_face_white_lm_coefs, "languagehindi")`$)
            *Tamil: ($`r reportCoefs(learning_face_white_lm_coefs, "languagetamil")`$)
            languagetamil:child_age: ($`r reportCoefs(learning_face_white_lm_coefs, "languagetamil:child_age")`$)
            languagegujarati:child_age: ($`r reportCoefs(learning_face_white_lm_coefs, "languagegujarati:child_age")`$)
            languagehindi:child_age: ($`r reportCoefs(learning_face_white_lm_coefs, "languagehindi:child_age")`$)
            
```{r diverging-barchart-colorway1}
ld <- l %>% filter(!is.na(rating_num)) %>%
              group_by(language) %>%
              mutate(mean_rating = na.mean(rating_num),
                     sd_rating = sd(rating_num, na.rm=T),
                     by_lang_z = (rating_num-mean_rating)/sd_rating,
                     rating_type=ifelse(by_lang_z < 0, "below", "above")) %>%
              group_by(language, face, rating_type) %>%
              summarize(sum=sum(by_lang_z))

ld$rating_type <- factor(ld$rating_type, levels=c("below", "above"),
                         labels=c("Below Average", "Above Average"))

ggplot(ld, 
       aes(x=fct_rev(face), y=sum)) + 
  geom_bar(stat="identity", aes(fill=rating_type), width=.5)  +
  scale_fill_manual(name="Learning Potential", 
                    #labels = c("Below Average", "Above Average"), 
                    values = c("gray65", "#31a354")) + 
  facet_wrap(~language, ncol=3) +
  xlab("Face") +
  #ylim(-100, 100) +
  ylab("Normalized Rating") +
  sans_axes_theme +
  theme(axis.text.y=element_text(size=8, color="gray30", 
                                 family="sans"),
        #legend.text = element_text(size=10),
        #legend.title = element_text(size=10),
        legend.position = "bottom") +
  coord_flip() 

ggsave("learning_diverging_barplot.png", device = "png", 
       path = "plots/final/",
       scale = 1, width = 7, height = 5, units = "in")
```

```{r diverging-barchart-colorway2}
ld$face_rating_type <- as.character(ld$rating_type)
ld[ld$rating_type=="Above Average",]$face_rating_type <- 
  paste("Above Average:\n", ld[ld$rating_type=="Above Average",]$face)

ld$face_rating_type <- factor(ld$face_rating_type, 
                               levels=c("Below Average", "Above Average:\n HINDU",
                                        "Above Average:\n MUSLIM",
                                        "Above Average:\n DRAVIDIAN",
                                        "Above Average:\n WHITE",
                                        "Above Average:\n ASIAN"),
                               labels=c("Below Average", "Above Average:\n HINDU",
                                        "Above Average:\n MUSLIM",
                                        "Above Average:\n DRAVIDIAN",
                                        "Above Average:\n WHITE",
                                        "Above Average:\n ASIAN"))

face_rating_type_colors <- c(
  "Below Average" = "gray65",
  "Above Average:\n HINDU" = "#1b9e77", # teal
  "Above Average:\n MUSLIM" = "#7570b3", # purple
  "Above Average:\n DRAVIDIAN" = "#e7298a", # magenta
  "Above Average:\n WHITE" = "#e6ab02", # goldenrod 
  "Above Average:\n ASIAN" = "#d95f02" # burnt orange
)

ldc <- ggplot(ld, 
       aes(x=fct_rev(face), y=sum)) + 
  geom_bar(stat="identity", aes(fill=face_rating_type), width=.5)  +
  scale_fill_manual(name="Estimated\nLearning\nPotential", 
                    values=face_rating_type_colors) + 
    scale_fill_manual(name="Predicted\nLearning:", 
                    values=face_rating_type_colors) + 
  facet_wrap(~language, ncol=3) +
  xlab("Face") +
  #ylim(-100, 100) +
  ylab("Normalized Learning Rating") +
  sans_axes_theme_bigger +
  theme(axis.text.y=element_text(size=10, color="gray30", 
                                 family="sans"),
       # axis.title.y=element_text(size=11),
        legend.text = element_text(size=10),
        legend.title = element_text(size=11),
        legend.key = element_rect(color=NA),
        legend.position = "bottom") +
  coord_flip() 

ggsave("learning_diverging_barplot_colored.png", device = "png", 
       path = "plots/barplots_overall/",
       scale = 1, width = 7, height = 5, units = "in")

ggsave(file="learning_diverging_barplot_colored.svg", plot=ldc, 
       path = "plots/barplots_overall/",
       scale = 1, width = 7, height = 5, units = "in")
```

```{r l-age-lineplot}
coefs <- l %>% 
    group_by(language, face) %>% 
    do({
      mod = lm(rating_num ~ child_age_centered, data = .)
      data.frame(intercept = coef(mod)[1],
                 slope = coef(mod)[2])
    })

ls <- merge(l, coefs, by=c("language", "face"))

ls$abs_slope <- abs(ls$slope)
ls$alpha_slope <- scale(ls$slope)/2.2
ls$alpha_slope <-  abs(ls$alpha_slope)
  
la <- ggplot(ls, aes(child_age, rating_num, color=face, 
                    fill=face, lty=face)) +
  stat_smooth(method="lm", level=.75, fullrange=T, 
              aes(alpha=alpha_slope)) +
    stat_smooth(method="lm", level=.75, fullrange=T, 
              se=F) +
    scale_color_manual(values=face_colors, name="") +
    scale_fill_manual(values=face_colors, name="") +
    scale_linetype_manual(values=face_ltys, name="") +
    facet_wrap(~language, ncol=3) +
   # ylim(-1, 2) +
    scale_y_continuous(limits=c(-0, 2.1), breaks=c(0, 1, 2),
                    label=c("0%", "50%", "100%")) +
    scale_alpha_identity(guide=F) +
    ylab("Mean Predicted Learning") + 
    xlab("Child Age (years)") +
    sans_axes_theme_bigger +
  
  theme(legend.position = "bottom")#,
       # axis.title.y=element_text(margin=margin(0,-5,0,0)))

ggsave(file="learning_age_lms.svg", 
       plot=la, 
       path = "plots/by_age/",
       scale = 1, width = 7, height = 5)
```

```{r}
cl <- ggarrange(la + theme(legend.position = "none",
                           axis.title.y=element_text(margin=margin(0,-10,0,0))), 
                ldc + theme(legend.position = "none",
                            axis.title.y=element_text(margin=margin(0,-5,0,0))), 
                labels='AUTO', widths = c(3, 4), 
            ncol = 2, nrow = 1, align = 'v')

ggsave("combined_learning_labeled.svg", cl, path="plots/combined/",
       width = 190, scale=2, units ='mm')
```


## LMERs
```{r l-lmer}
l_lmer <- lmer(rating ~ face*language+child_age_centered + (1|id), l)
summary(l_lmer) 
Anova(l_lmer)
l_lm <- lm(rating ~ face*language+child_age_centered, l)
```

```{r l-lmer-3way-int}
l_lmer <- lmer(rating ~ face*language*child_age_centered + (1|id), l)
summary(l_lmer)
Anova(l_lmer)
View(summary(l_lmer))
```

## Gujarati
```{r}
g_ord_mod <- clmm(rating_cat ~ (1|id) + face*child_age_centered,
  link="logit", data = l[l$language=='"Gujarati"', ])

g_noint_ord_mod <- clmm(rating_cat ~ (1|id) + face + child_age_centered,
  link="logit", data = l[l$language=='"Gujarati"', ])

anova(g_noint_ord_mod, g_ord_mod, test="LRT")
```

```{r g-ord-tab}
sjPlot::tab_model(
      g_ord_mod, 
      show.r2 = TRUE, 
      show.icc = FALSE, 
      show.re.var = FALSE, 
      p.style = "numeric_stars", 
      emph.p = TRUE, 
      file = "tables/models/primary/learn_ord_mod_gujarati.html")

go_df <- readHTMLTable(here('4_learning/tables/models/primary/learn_ord_mod_gujarati.html'), header=T) 

go_df <- as.data.frame(go_df)
names(go_df) <- go_df[1,]
go_df <- go_df[-1,]

print.xtable(go_df, type="latex", file="tables/models/primary/learn_ord_mod_gujarati.tex")
```

## Hindi
```{r}
h_ord_mod <- clmm(rating_cat ~ (1|id) + face*child_age_centered,
  link="logit", data = l[l$language=='"Hindi"', ])

h_noint_ord_mod <- clmm(rating_cat ~ (1|id) + face + child_age_centered,
  link="logit", data = l[l$language=='"Hindi"', ])

anova(h_noint_ord_mod, h_ord_mod, test="LRT")
```

```{r h-ord-tab}
sjPlot::tab_model(
      h_ord_mod, 
      show.r2 = TRUE, 
      show.icc = FALSE, 
      show.re.var = FALSE, 
      p.style = "numeric_stars", 
      emph.p = TRUE, 
      file = "tables/models/primary/learn_ord_mod_hindi.html")

ho_df <- readHTMLTable(here('4_learning/tables/models/primary/learn_ord_mod_hindi.html'), header=T) 

ho_df <- as.data.frame(ho_df)
names(ho_df) <- ho_df[1,]
ho_df <- ho_df[-1,]

print.xtable(ho_df, type="latex", file="tables/models/primary/learn_ord_mod_hindi.tex")
```

## Tamil
```{r}
t_ord_mod <- clmm(rating_cat ~ (1|id) + face*child_age_centered,
  link="logit", data = l[l$language=='"Tamil"', ])

t_noint_ord_mod <- clmm(rating_cat ~ (1|id) + face + child_age_centered,
  link="logit", data = l[l$language=='"Tamil"', ])

anova(t_noint_ord_mod, t_ord_mod, test="LRT")
```

```{r t-ord-tab}
sjPlot::tab_model(
      t_ord_mod, 
      show.r2 = TRUE, 
      show.icc = FALSE, 
      show.re.var = FALSE, 
      p.style = "numeric_stars", 
      emph.p = TRUE, 
      file = "tables/models/primary/learn_ord_mod_tamil.html")

to_df <- readHTMLTable(here('4_learning/tables/models/primary/learn_ord_mod_tamil.html'), header=T) 

to_df <- as.data.frame(to_df)
names(to_df) <- to_df[1,]
to_df <- to_df[-1,]

print.xtable(to_df, type="latex", file="tables/models/primary/learn_ord_mod_tamil.tex")
```

```{r tamil-fam, warning=F}
i <- read.csv(here('data/r_dfs/subsets/language_familiarity.csv'))

tli <- merge(l, i, by=c("army_navy_language", "id")) %>%
  filter(army_navy_language=="tamil")

tli_mod <- clmm(rating_cat ~ (1|id) + face*familiar + child_age_centered, link="logit", tli)

tli_mod_null <- clmm(rating_cat ~ (1|id) + face + familiar + child_age_centered, link="logit", tli)

anova(tli_mod, tli_mod_null, test = "Chisq")
summary(tli_mod)
```

## Mandarin
```{r}
c_ord_mod <- clmm(rating_cat ~ (1|id) + face + child_age_centered,
  link="logit", data = l[l$language=='"Chinese"', ])
```

```{r c-ord-tab}
sjPlot::tab_model(
      c_ord_mod, 
      show.r2 = TRUE, 
      show.icc = FALSE, 
      show.re.var = FALSE, 
      p.style = "numeric_stars", 
      emph.p = TRUE, 
      file = "tables/models/primary/learn_ord_mod_mandarin.html")

co_df <- readHTMLTable(here('4_learning/tables/models/primary/learn_ord_mod_mandarin.html'), header=T) 

co_df <- as.data.frame(co_df)
names(co_df) <- co_df[1,]
co_df <- co_df[-1,]

print.xtable(co_df, type="latex", file="tables/models/primary/learn_ord_mod_mandarin.tex")
```

```{r chinese-fam, warning=F}
i <- read.csv(here('data/r_dfs/subsets/language_familiarity.csv'))

cli <- merge(l, i, by=c("army_navy_language", "id")) %>%
  filter(army_navy_language=="chinese")

cli_mod <- clmm(rating_cat ~ (1|id) + face*familiar + child_age_centered, link="logit", cli)

cli_mod_null <- clmm(rating_cat ~ (1|id) + face + familiar + child_age_centered, link="logit", cli)

anova(cli_mod, cli_mod_null, test = "Chisq")
summary(cli_mod)
```

```{r c-fam-tab}
sjPlot::tab_model(
      cli_mod, 
      show.r2 = TRUE, 
      show.icc = FALSE, 
      show.re.var = FALSE, 
      p.style = "numeric_stars", 
      emph.p = TRUE, 
      file = "tables/models/familiarity/learn_fam_mandarin.html")
```

## English
```{r}
e_ord_mod <- clmm(rating_cat ~ (1|id) + face*child_age_centered,
  link="logit", data = l[l$language=='"English"', ])
lalt <- l
lalt$face <- relevel(lalt$face, ref="DRAVIDIAN")
e_ord_modalt <- clmm(rating_cat ~ (1|id) + face*child_age_centered,
  link="logit", data = lalt[lalt$language=='"English"', ])

e_noint_ord_mod <- clmm(rating_cat ~ (1|id) + face + child_age_centered,
  link="logit", data = l[l$language=='"English"', ])

anova(e_noint_ord_mod, e_ord_mod, test="LRT")
```

```{r e-ord-tab}
sjPlot::tab_model(
      e_ord_mod, 
      show.r2 = TRUE, 
      show.icc = FALSE, 
      show.re.var = FALSE, 
      p.style = "numeric_stars", 
      emph.p = TRUE, 
      file = "tables/models/primary/learn_ord_mod_english.html")

eo_df <- readHTMLTable(here('4_learning/tables/models/primary/learn_ord_mod_english.html'), header=T) 

eo_df <- as.data.frame(eo_df)
names(eo_df) <- eo_df[1,]
eo_df <- eo_df[-1,]

print.xtable(eo_df, type="latex", file="tables/models/primary/learn_ord_mod_english.tex")
```

```{r}
id_glm <- glm(id_correct ~ 0 +
                    language*child_age_centered, 
                  family="binomial", i)

id_glm_null <- glm(id_correct ~ 0 +
                    language + child_age_centered, 
                  family="binomial", i)

anova(id_glm_null, id_glm, test="Chisq")

sjPlot::tab_model(
      id_glm, 
      show.r2 = TRUE, 
      show.icc = FALSE, 
      show.re.var = FALSE, 
      p.style = "numeric_stars", 
      emph.p = TRUE)

```